\documentclass[../../main]{subfiles}
\pagestyle{fancy}

\begin{document}

\chapter{Set-theoretic connections}
\thispagestyle{fancy}

\section{Games}

\subsection{The finite case}

In this section we are going to consider properties of the $n$-Ramsey cardinals for finite $n$. Note in particular that the $\G_n^\theta(\kappa)$ games are determined, making the ``strategic'' adjective superfluous in this case. We further note that the $\theta$'s are also dispensible in this finite case:

\prop[N.]{
	Let $\kappa<\theta$ be regular cardinals and $n<\omega$. Then player II has a winning strategy in $\G_n^\theta(\kappa)$ iff they have a winning strategy in the game $\G_n(\kappa)$, which is defined as $\G_n^\theta(\kappa)$ except that we don't require that $\M_n\prec H_\theta$.
}
\proof{
	$\Leftarrow$ is clear, so assume that II has a winning strategy $\tau$ in $\G_n^\theta(\kappa)$. Whenever player I plays $\M_k$ in $\G_n(\kappa)$ for $k\leq n$ then define $\M_k^*:=\hull^{H_\theta}(\P)$ where $\P\cong\M_k$ is the transitive collapse of $\M_k$, and play $\M_k^*$ in $\G_n^\theta(\kappa)$. Let $\mu_k$ be the $\tau$-responses to the $\M_k^*$'s and let player II play the $\mu_k$'s in $\G_n(\kappa)$ as well.

	\qquad Assume that this new strategy isn't winning for player II in $\G_n(\kappa)$, so that $\ult(\M_n,\mu_n)$ is illfounded. This is witnessed by some $\omega$-sequence $\vec f:=\bra{f_k\mid k<\omega}$ of $f_k\in{^\kappa o(\M_n)}\cap\M_n$ with $X_k:=\{\alpha<\kappa\mid f_{k+1}(\alpha)<f_k(\alpha)\}\in\mu_n$ for all $k<\omega$. Let $\nu\gg\kappa$, $\h:=\chull^{H_\nu}(\M_n\cup\{\vec f,\M_n,\mu_n\})$ be the transitive collapse of the Skolem hull $\hull^{H_\nu}(\M_n\cup\{\vec f,\M_n,\mu_n\})$, and $\pi:\h\to H_\nu$ be the uncollapse; write $\bar x:=\pi^{-1}(x)$ for all $x\in\ran\pi$.

	\qquad Now $\bar A=A$ for every $A\in\p(\kappa)\cap\M_n$ and thus also $\bar\mu_n=\mu_n$. But now the $\bar f_k$'s witness that $\ult(\bar\M_n,\mu_n)$ is illfounded and thus also that $\ult(\M_n^*,\mu_n)$ is illfounded since $\M_n^*=\hull^{H_\theta}(\bar\M_n)$, contradicting that $\tau$ is winning.
}

For this reason we'll work with the $\G_n(\kappa)$ games throughout this section. Since we don't have to deal with the $\theta$'s anymore we note that $n$-Ramseyness can now be described using a $\Pi^1_{2n+2}$-formula and normal $n$-Ramseyness using a $\Pi^1_{2n+3}$-formula.

\qquad We already have the following characterisations, as proven in \cite{Abramson}.

\theo[Abramson et al.]{
	Let $\kappa=\kappa^{<\kappa}$ be a cardinal. Then
	\begin{enumerate}
		\item $\kappa$ is weakly compact if and only if it is $0$-Ramsey;
		\item $\kappa$ is weakly ineffable if and only if it is genuine $0$-Ramsey;
		\item $\kappa$ is ineffable if and only if it is normal $0$-Ramsey.
	\end{enumerate}
}
\proof{
	This is mostly a matter of changing terminology from \cite{Abramson} to the current game-theoretic one, so we only show $(i)$. Theorem 1.1.3 in \cite{Abramson} shows that $\kappa$ is weakly compact if and only if every $\kappa$-sized collection of subsets of $\kappa$ is measured by a ${<}\kappa$-complete measure, in the sense that every ${<}\kappa$-sequence (in $V$) of measure one sets has non-empty intersection.
	
	\qquad For the $\Rightarrow$ direction we can let player II respond to any $\M_0$ by first getting the ${<}\kappa$-complete $\M_0$-measure $\nu_0$ on $\kappa$ from the above-mentioned result, forming the (well-founded) ultrapower $\pi:\M_0\to\ult(\M_0,\nu)$ and then playing the derived measure of $\pi$, which is $\M_0$-normal and good. For $\Leftarrow$, if $X\subset\p(\kappa)$ has size $\kappa$ then, using that $\kappa=\kappa^{<\kappa}$, we can find a $\kappa$-model $\M_0\prec H_\theta$ with $X\subset\M_0$. Letting player I play $\M_0$ in $\G_0(\kappa)$ we get some $\M_0$-normal good $\M_0$-measure $\mu_0$ on $\kappa$. Since $\M_0$ is closed under ${<}\kappa$-sequences we get that $\mu_0$ is ${<}\kappa$-complete.
}


\subsection*{Indescribability}

In this section we aim to prove that $n$-Ramseys are $\Pi^1_{2n+1}$-indescribable and that normal $n$-Ramseys are $\Pi^1_{2n+2}$-indescribable, which will also establish that the hierarchy of alternating $n$-Ramseys and normal $n$-Ramseys forms a strict hierarchy. Recall the following definition.

\defi{
	A cardinal $\kappa$ is \textbf{$\Pi^1_n$-indescribable} if whenever $\varphi(v)$ is a $\Pi_n$ formula, $X\subset V_\kappa$ and $V_{\kappa+1}\models\varphi[X]$, then there is an $\alpha<\kappa$ such that $V_{\alpha+1}\models\varphi[X\cap V_\alpha]$.
}

Our first indescribability result is then the following, where the $n=0$ case is inspired by the proof of weakly compact cardinals being $\Pi^1_1$-indescribable --- see \cite{Abramson}.

\theo[N.]{
  \label{theo.ind}
	Every $n$-Ramsey $\kappa$ is $\Pi^1_{2n+1}$-indescribable for $n<\omega$.
}
\proof{
  Let $\kappa$ be $n$-Ramsey and assume that it is not $\Pi^1_{2n+1}$-indescribable, witnessed by a $\Pi_{2n+1}$-formula $\varphi(v)$ and a subset $X\subset V_\kappa$, meaning that $V_{\kappa+1}\models\varphi[X]$ and, for every $\alpha<\kappa$, $V_{\alpha+1}\models\lnot\varphi[X\cap V_\alpha]$. We will deal with the $(2n+1)$-many quantifiers occuring in $\varphi$ in $(n+1)$-many steps. We will here describe the first two steps with the remaining steps following the same pattern.

\qquad \framebox{\textbf{First step.}} Write $\varphi(v)\equiv\forall v_1\psi(v,v_1)$ for a $\Sigma_{2n}$-formula $\psi(v,v_1)$. As we are assuming that $V_{\alpha+1}\models\lnot\varphi[X\cap V_\alpha]$ holds for every $\alpha<\kappa$, we can pick witnesses $A^{(0)}_\alpha\subset V_\alpha$ to the outermost existential quantifier in $\lnot\varphi[X\cap V_\alpha]$.

\qquad Let $\M_0$ be a weak $\kappa$-model such that $V_\kappa\subset\M_0$ and $\vec A^{(0)},X\in\M_0$. Fix a good $\M_0$-normal $\M_0$-measure $\mu_0$ on $\kappa$, using the $0$-Ramseyness of $\kappa$. Form $\mathcal A^{(0)}:=[\vec A^{(0)}]_{\mu_0}\in\ult(\M_0,\mu_0)$, where we without loss of generality may assume that the ultrapower is transitive. $\M_0$-normality of $\mu_0$ implies that $\mathcal A^{(0)}\subset V_\kappa$, so that we have that $V_{\kappa+1}\models\psi[X,\mathcal A^{(0)}]$. Now \L o\' s' Lemma, $\M_0$-normality of $\mu_0$ and $V_\kappa\subset\M_0$ also ensures that
\eq{
  \ult(\M_0,\mu_0)\models\godel{V_{\kappa+1}\models\lnot\psi[X,\mathcal A^{(0)}]}.\tag*{$(1)$}
}

This finishes the first step. Note that if $n=0$ then $\lnot\psi$ would be a $\Delta_0$-formula, so that $(1)$ would be absolute to the true $V_{\kappa+1}$, yielding a contradiction. If $n>0$ we cannot yet conclude this however, but that is what we are aiming for in the remaining steps.\\

\qquad \framebox{\textbf{Second step.}} Write $\psi(v,v_1)\equiv\exists v_2\forall v_3\chi(v,v_1,v_2,v_3)$ for a $\Sigma_{2(n-1)}$-formula $\chi(v,v_1,v_2,v_3)$. Since we have established that $V_{\kappa+1}\models\psi[X,\mathcal A^{(0)}]$ we can pick some $B^{(0)}\subset V_\kappa$ such that
\eq{
  V_{\kappa+1}\models\forall v_3\chi[X,\mathcal A^{(0)},B^{(0)},v_3]\tag*{$(2)$}
}

which then also means that, for every $\alpha<\kappa$,
\eq{
  V_{\alpha+1}\models\exists v_3\lnot\chi[X\cap V_\alpha,A^{(0)}_\alpha,B^{(0)}\cap V_\alpha,v_3].\tag*{$(3)$}
}

Fix witnesses $A^{(1)}_\alpha\subset V_\alpha$ to the existential quantifier in $(3)$ and define the sets
\eq{
  S_\alpha^{(0)}:=\{\xi<\kappa\mid A_\xi^{(0)}\cap V_\alpha=\mathcal A^{(0)}\cap V_\alpha\}
}

for every $\alpha<\kappa$ and note that $S_\alpha^{(0)}\in\mu_0$ for every $\alpha<\kappa$, since $V_\kappa\subset\M_0$ ensures that $\mathcal A^{(0)}\cap V_\alpha\in\M_0$ and $\M_0$-normality of $\mu_0$ then implies that $S_\alpha^{(0)}\in\mu_0$ is equivalent to
\eq{
  \ult(\M_0,\mu_0)\models\mathcal A^{(0)}\cap V_\alpha=\mathcal A^{(0)}\cap V_\alpha,
}

which is clearly the case. Now let $\M_1\supset\M_0$ be a weak $\kappa$-model such that $\mathcal A^{(0)},\vec A^{(1)},\vec S^{(0)},B^{(0)}\in\M_1$. Let $\mu_1\supset\mu_0$ be an $\M_1$-normal $\M_1$-measure on $\kappa$, using the $1$-Ramseyness of $\kappa$, so that $\M_1$-normality of $\mu_1$ yields that $\triangle\vec S^{(0)}\in\mu_1$. Observe that $\xi\in\triangle\vec S^{(0)}$ if and only if $A^{(0)}_\xi\cap V_\alpha=\mathcal A^{(0)}\cap V_\alpha$ for every $\alpha<\xi$, so if $\xi$ is a limit ordinal then it holds that $A^{(0)}_\xi=\mathcal A^{(0)}\cap V_\xi$. Now, as before, form $\mathcal A^{(1)}:=[\vec A^{(1)}]_{\mu_1}\in\ult(\M_1,\mu_1)$, so that $(2)$ implies that
\eq{
  V_{\kappa+1}\models\chi[X,\mathcal A^{(0)},B^{(0)},\mathcal A^{(1)}]
}

and the definition of the $A_\alpha^{(1)}$'s along with $(3)$ gives that, for every $\alpha<\kappa$,
\eq{
  V_{\alpha+1}\models\lnot\chi[X\cap V_\alpha,A_\alpha^{(0)},B^{(0)}\cap V_\alpha,A_\alpha^{(1)}].
}

Now this, paired with the above observation regarding $\triangle\vec S^{(0)}$, means that for every $\alpha\in\triangle\vec S^{(0)}\cap\text{Lim}$ we have that
\eq{
  V_{\alpha+1}\models\lnot\chi[X\cap V_\alpha,\mathcal A^{(0)}\cap V_\alpha,B^{(0)}\cap V_\alpha,A_\alpha^{(1)}],
}

so that $\M_1$-normality of $\mu_1$ and \L o\' s' lemma implies that
\eq{
  \ult(\M_1,\mu_1)\models\godel{V_{\kappa+1}\models\lnot\chi[X,\mathcal A^{(0)},B^{(0)},\mathcal A^{(1)}]}.
}

This finishes the second step. Continue in this way for a total of $(n+1)$-many steps, ending with a $\Delta_0$-formula $\phi(v,v_1,\hdots,v_{2n+1})$ such that
\eq{
	V_{\kappa+1}\models\phi[X,\mathcal A^{(0)},B^{(0)},\hdots,\mathcal A^{(n-1)},B^{(n-1)},\mathcal A^{(n)}]\tag*{$(4)$}
}

and that $\ult(\M_n,\mu_n)\models\godel{V_{\kappa+1}\models\lnot\phi[X,\mathcal A^{(0)},B^{(0)},\hdots,\mathcal A^{(n)}]}$. But now absoluteness of $\lnot\phi$ means that $V_{\kappa+1}\models\lnot\phi[X,\mathcal A^{(0)},B^{(0)},\hdots,\mathcal A^{(n)}]$, contradicting $(4)$.
}

Note that this is optimal, as $n$-Ramseyness can be described by a $\Pi^1_{2n+2}$-formula. As a corollary we then immediately get the following.

\qcoro[N.]{
	\label{coro.ind}
	Every ${<}\omega$-Ramsey cardinal is $\Delta^2_0$-indescribable.
}

The second indescribability result concerns the normal $n$-Ramseys, where the $n=0$ case here is inspired by the proof of ineffable cardinals being $\Pi^1_2$-indescribable --- see \cite{Abramson}.

\theo[N.]{
	\label{theo.normind}
	Every normal $n$-Ramsey $\kappa$ is $\Pi^1_{2n+2}$-indescribable for $n<\omega$.
}

Before we commence with the proof, note that we cannot simply do the same thing as we did in the proof of Theorem \ref{theo.ind}, as we would end up with a $\Pi^1_1$ statement in an ultrapower, and as $\Pi^1_1$ statements are not upwards absolute in general we would not be able to get our contradiction.\\

\proof{
	Let $\kappa$ be normal $n$-Ramsey and assume that it is not $\Pi^1_{2n+2}$-indescribable, witnessed by a $\Pi_{2n+2}$-formula $\varphi(v)$ and a subset $X\subset V_\kappa$. Use that $\kappa$ is $n$-Ramsey to perform the same $n+1$ steps as in the proof of Theorem \ref{theo.ind}. This gives us a $\Sigma_1$-formula $\phi(v,v_1,\hdots,v_{2n+1})$ along with sequences $\bra{\mathcal A^{(0)},\cdots,\mathcal A^{(n)}}$, $\bra{B^{(0)},\hdots,B^{(n-1)}}$ and a play $\bra{\M_k,\mu_k\mid k\leq n}$ of $\G_n(\kappa)$ in which player II wins and $\mu_n$ is normal, such that
\eq{
  V_{\kappa+1}\models\phi[X,\mathcal A^{(0)},B^{(0)},\hdots,\mathcal A^{(n-1)},B^{(n-1)},\mathcal A^{(n)}]\tag*{$(1)$}
}

and, for $\mu_n$-many $\alpha<\kappa$,
\eq{
  V_{\alpha+1}\models\lnot\phi[X\cap V_\alpha,\mathcal A^{(0)}\cap V_\alpha,B^{(0)}\cap V_\alpha,\hdots,\mathcal A^{(n-1)}\cap V_\alpha,B^{(n-1)}\cap V_\alpha,A^{(n)}_\alpha].
}

Now form $S^{(n)}_\alpha\in\mu_n$ as in the proof of Theorem \ref{theo.ind}. The main difference now is that we do not know if $\vec S^{(n)}\in\M_n$ (in the proof of Theorem \ref{theo.ind} we only ensured that $\vec S^{(k)}\in\M_{k+1}$ for every $k<n$ and we only defined $\vec S^{(k)}$ for $k<n$), but we can now use normality\footnote{Recall that this is stronger than just requiring it to be $\M_n$-normal --- we don't require $\vec S^{(n)}\in\M_n$.} of $\mu_n$ to ensure that we \textit{do} have that $\triangle\vec S^{(n)}$ is stationary in $\kappa$. This means that we get a stationary set $S\subset\kappa$ such that for every $\alpha\in S$ it holds that
\eq{
  V_{\alpha+1}\models\lnot\phi[X\cap V_\alpha,\mathcal A^{(0)}\cap V_\alpha,B^{(0)}\cap V_\alpha,\hdots, B^{(n-1)}\cap V_\alpha,\mathcal A^{(n)}\cap V_\alpha].\tag*{$(2)$}
}

Now note that since $\kappa$ is inaccessible it is $\Sigma^1_1$-indescribable, meaning that we can reflect $(1)$. Furthermore, Lemma 3.4.3 of \cite{Abramson} shows that the set of reflection points of $\Sigma^1_1$-formulas is in fact club, so intersecting this club with $S$ we get a $\zeta\in S$ satisfying that
\eq{
  V_{\zeta+1}\models\phi[X\cap V_\zeta,\mathcal A^{(0)}\cap V_\zeta,B^{(0)}\cap V_\zeta,\hdots, B^{(n-1)}\cap V_\zeta,\mathcal A^{(n)}\cap V_\zeta],
}

contradicting $(2)$.
}

Note that this is optimal as well, since normal $n$-Ramseyness can be described by a $\Pi^1_{2n+3}$-formula. In particular this then means that every $(n{+}1)$-Ramsey is a normal $n$-Ramsey stationary limit of normal $n$-Ramseys, and every normal $n$-Ramsey is an $n$-Ramsey stationary limit of $n$-Ramseys, making the hierarchy of alternating $n$-Ramseys and normal $n$-Ramseys a strict hierarchy.


\subsection*{Downwards absoluteness to $L$}

The following proof is basically the proof of Theorem 4.1.1 in \cite{Abramson}.

\theo[N.]{
	Genuine- and normal $n$-Ramseys are downwards absolute to $L$, for every $n<\omega$.
}
\proof{
	Assume first that $n=0$ and that $\kappa$ is a genuine $0$-Ramsey cardinal. Let $\M\in L$ be a weak $\kappa$-model --- we want to find a genuine $\M$-measure inside $L$. By assumption we \textit{can} find such a measure $\mu$ in $V$; we will show that in fact $\mu\in L$. Fix any enumeration $\bra{A_\xi\mid\xi<\kappa}\in L$ of $\p(\kappa)\cap\M$. It then clearly suffices to show that $T\in L$, where $T:=\{\alpha<\kappa\mid A_\xi\in\mu\}$.

  \clai{
		\label{clai.pospart}
		$T\cap\alpha\in L$ for any $\alpha<\kappa$.
	}

	\cproof{
		Let $\vec B$ be the \textbf{$\mu$-positive part} of $\vec A$, meaning that $B_\xi:=A_\xi$ if $A_\xi\in\mu$ and $B_\xi:=\lnot A_\xi$ if $A_\xi\notin\mu$. As $\mu$ is genuine we get that $\triangle\vec B$ has size $\kappa$, so we can pick $\delta\in\triangle\vec B$ with $\delta>\alpha$. Then $T\cap\alpha=\{\xi<\alpha\mid\delta\in A_\xi\}$, which can be constructed within $L$.
	}

	But now Lemma 4.1.2 in \cite{Abramson} shows that there is a $\Pi_1$ formula $\varphi(v)$ such that, given any non-zero ordinal $\zeta$, $V_{\zeta+1}\models\varphi[A]$ if and only if $\zeta$ is a regular cardinal and $A$ is a non-constructible subset of $\zeta$. If we therefore assume that $T\notin L$ then $V_{\kappa+1}\models\varphi[T]$, which by $\Pi^1_1$-indescribability of $\kappa$ means that there exists some $\alpha<\kappa$ such that $V_{\alpha+1}\models\varphi[T\cap V_\alpha]$, i.e. that $T\cap\alpha\notin L$, contradicting the claim. Therefore $\mu\in L$. It is still genuine in $L$ as $(\triangle\mu)^L=\triangle\mu$, and if $\mu$ was normal then that is still true in $L$ as clubs in $L$ are still clubs in $V$. The cases where $\kappa$ is a genuine- or normal $n$-Ramsey cardinal is analogous.
}

Since $(n{+}1)$-Ramseys are normal $n$-Ramseys we then immediately get the following.

\qcoro[N.]{
	Every $(n{+}1)$-Ramsey is normal $n$-Ramsey in $L$, for every $n<\omega$. In particular, ${<}\omega$-Ramseys are downwards absolute to $L$.
}


\subsection*{Complete ineffability}

In this section we provide a characterisation of the \textit{completely ineffable} cardinals in terms of the $\alpha$-Ramseys. To arrive at such a characterisation, we need a slight strengthening of the ${<}\omega$-Ramsey cardinals, namely the \textit{coherent ${<}\omega$-Ramseys} as defined in \ref{defi.cohramsey}. Note that a coherent ${<}\omega$-Ramsey is precisely a cardinal satisfying the $\omega$-filter property, as defined in \cite{HolySchlicht}.

\qquad The following theorem shows that assuming coherency does yield a strictly stronger large cardinal notion. The idea of its proof is very closely related to the proof of Theorem \ref{theo.normind} (the indescribability of normal $n$-Ramseys), but the main difference is that we want everything to occur locally inside our weak $\kappa$-models.

\theo[N.]{
	Every coherent ${<}\omega$-Ramsey is a stationary limit of ${<}\omega$-Ramseys.
}
\proof{
	Let $\kappa$ be coherent ${<}\omega$-Ramsey. Let $\theta\gg\kappa$ be regular and let $\M_0\prec H_\theta$ be a weak $\kappa$-model with $V_\kappa\subset\M_0$. Let then player I play arbitrarily while player II plays according to her coherent winning strategies in $\G_n(\kappa)$, yielding a weak $\kappa$-model $\M\prec H_\theta$ with an $\M$-normal $\M$-measure $\mu:=\bigcup_{n<\omega}\mu_n$ on $\kappa$.
		
	\qquad Assume towards a contradiction that $X:=\{\xi<\kappa\mid\xi\text{ is ${<}\omega$-Ramsey}\}\notin\mu$. Since $X=\bigcap\vec X$ and $\vec X\in\M$, where $X_n:=\{\xi<\kappa\mid\xi\text{ is $n$-Ramsey}\}$, we must have by $\M$-normality of $\mu$ that $\lnot X_k\in\mu$ for some $k<\omega$. Note that $\lnot X_k\in\M_0$ by elementarity, so that $\lnot X_k\in\mu_0$ as well. Perform the $k+1$ steps as in the proof of Theorem \ref{theo.normind} with $\varphi(\xi)$ being $\godel{\xi\text{ is $k$-Ramsey}}$, so that we get a weak $\kappa$-model $\M_{k+1}\prec H_\theta$, an $\M_{k+1}$-normal $\M_{k+1}$-measure $\tilde\mu_{k+1}$ on $\kappa$, a $\Sigma_1$-formula $\varphi(v,v_1,v_2,\hdots,v_{2k+1})$ and sequences $\bra{\mathcal A^{(0)},\hdots,\mathcal A^{(k)}}$ and $\bra{B^{(0)},\hdots,B^{(k-1)}}$ such that
	\eq{
		V_{\kappa+1}\models\varphi[\kappa,\mathcal A^{(0)},B^{(0)},\mathcal A^{(1)},B^{(1)},\hdots,\mathcal A^{(k-1)},B^{(k-1)},\mathcal A^{(k)}]\tag*{$(2)$}
	}

	and there is a $Y\in\tilde\mu_{k+1}$ with $Y\subset\lnot X_k$ such that given any $\xi\in Y$,
	\eq{
		V_{\xi+1}\models\lnot\varphi[\xi,A_\xi^{(0)},B^{(0)}\cap V_\xi,A^{(1)}_\xi,B^{(1)}\cap V_\xi,\hdots,A^{(k-1)}_\xi,B^{(k-1)}\cap V_\xi,A^{(k)}_\xi]\tag*{$(3)$},
	}

	where $\mathcal A^{(i)}=[\vec A^{(i)}]_{\mu_i}\in\ult(\M_i,\mu_i)$ as in the proof of Theorem \ref{theo.ind}.

	\qquad Since $\kappa$ in particular is $\Sigma^1_1$-indescribable, Lemma 3.4.3 of \cite{Abramson} implies that we get a club $C\subset\kappa$ of reflection points of $(2)$. Let $\M_{k+2}\supset\M_{k+1}$ be a weak $\kappa$-model with $\mathcal A^{(k)}\in\M_{k+2}$, where the above $(n+1)$-steps ensured that the $B^{(i)}$'s and the remaining $\mathcal A^{(i)}$'s are all elements of $\M_{k+1}$. In particular, as $C$ is a definable subset in the $\mathcal A^{(i)}$'s and $B^{(i)}$'s we also get that $C\in\M_{k+2}$. Letting $\tilde\mu_{k+2}$ be the associated measure on $\kappa$, $\M_{k+2}$-normality of $\tilde\mu_{k+2}$ ensures that $C\in\tilde\mu_{k+2}$. Now define, for every $\alpha<\kappa$,
	\eq{
		S_\alpha:=\{\xi\in Y\mid\forall i\leq k:\mathcal A^{(i)}\cap V_\alpha=A^{(i)}_\xi\cap V_\alpha\}
	}

	and note that $S_\alpha\in\tilde\mu_{k+2}$ for every $\alpha<\kappa$. Write $\vec S:=\bra{S_\alpha\mid\alpha<\kappa}$ and note that since $\vec S$ is definable it is an element of $\M_{k+2}$ as well. Then $\M_{k+2}$-normality of $\tilde\mu_{k+2}$ ensures that $\triangle\vec S\in\tilde\mu_{k+2}$, so that $C\cap\triangle\vec S\in\tilde\mu_{k+2}$ as well. But letting $\zeta\in C\cap\triangle\vec S$ we see, as in the proof of Theorem \ref{theo.ind}, that
	\eq{
		V_{\zeta+1}\models\varphi[\zeta,A^{(0)}_\zeta,B^{(0)}\cap V_\zeta,A^{(1)}_\zeta,B^{(1)}\cap V_\zeta,\hdots,A^{(k)}_\zeta]
	}

	since $\triangle\vec S\subset Y$, contradicting $(3)$. Hence $X\in\mu$, and since $\M\prec H_\theta$ we have that $\M$ is correct about stationary subsets of $\kappa$, meaning that $\kappa$ is a stationary limit of ${<}\omega$-Ramseys.
}

Now, having established the strength of this large cardinal notion, we move towards complete ineffability. We recall the following definitions.

\defi{
	A collection $R\subset\p(\kappa)$ is a \textbf{stationary class} if
	\begin{enumerate}
		\item $R\neq\emptyset$;
		\item every $A\in R$ is stationary in $\kappa$;
		\item if $A\in R$ and $B\supset A$ then $B\in R$.
	\end{enumerate}
}

\defi{
	A cardinal $\kappa$ is \textbf{completely ineffable} if there is a stationary class $R$ such that for every $A\in R$ and $f:[A]^2\to 2$ there is an $H\in R$ homogeneous for $f$.
}

We then arrive at the following characterisation, influenced by the proof of Theorem 1.3.4 in \cite{Abramson}.

\theo[N.]{
	\label{theo.ineff}
	A cardinal $\kappa$ is completely ineffable if and only if it is coherent ${<}\omega$-Ramsey.
}
\proof{
	$(\Leftarrow)$: Assume $\kappa$ is coherent ${<}\omega$-Ramsey, witnessed by strategies $\bra{\tau_n\mid n<\omega}$. Let $f:[\kappa]^2\to 2$ be arbitrary and form the sequence $\bra{A_\alpha^f\mid\alpha<\kappa}$ as
	\eq{
		A_\alpha^f:=\{\beta>\alpha\mid f(\{\alpha,\beta\})=0\}.
	}

	Let $\M_f$ be a transitive weak $\kappa$-model with $\vec A^f\in\M_f$, and let $\mu_f$ be the associated $\M_f$-measure on $\kappa$ given by $\tau_0$.\footnote{Technically we would have to require that $\M_f\prec H_\theta$ for some regular $\theta>\kappa$ to be able to use $\tau_0$, but note that we could simply get a measure on $\hull^{H_\theta}(\M_f)$ and restrict it to $\M_f$. We will use this throughout the proof.} $1$-Ramseyness of $\kappa$ ensures that $\mu_f$ is normal, meaning $\triangle\mu_f$ is stationary in $\kappa$. Define a new sequence $\vec B^f$ as the $\mu_f$-positive part of $\vec A^f$.\footnote{The \textit{$\mu$-positive part} was defined in Claim \ref{clai.pospart}.} Then $B_\alpha^f\in\mu_f$ for all $\alpha<\kappa$, so that normality of $\mu_f$ implies that $\triangle\vec B^f$ is stationary.
	
	\qquad Let now $\M_f'$ be a new transitive weak $\kappa$-model with $\M_f\subset\M_f'$ and $\mu_f\in\M_f'$, and use $\tau_1$ to get an $\M_f'$-measure $\mu_f'\supset\mu_f$ on $\kappa$. Then $\triangle\vec B^f\cap\{\xi<\kappa\mid A_\xi^f\in\mu_f\}$ and $\triangle\vec B^f\cap\{\xi<\kappa\mid A_\xi^f\notin\mu_f\}$ are both elements of $\M_f'$, so one of them is in $\mu_f'$; set $H_f$ to be that one. Note that $H_f$ is now both stationary in $\kappa$ and homogeneous for $f$.

	\qquad Now let $g:[H_f]^2\to 2$ be arbitrary and again form
	\eq{
		A_\alpha^g:=\{\beta\in H_f\mid\beta>\alpha\land g(\{\alpha,\beta\})=0\}
	}
	
	for $\alpha\in H_f$. Let $\M_{f,g}\supset\M_f'$ be a transitive weak $\kappa$-model with $\vec A^g\in\M_{f,g}$ and use $\tau_2$ to get an $\M_{f,g}$-measure $\mu_{f,g}\supset\mu_f'$ on $\kappa$. As before we then get a stationary $H_{f,g}\in\mu_{f,g}'$ which is homogeneous for $g$. We can continue in this fashion since $\tau_n\subset\tau_{n+1}$ for all $n<\omega$. Define then
	\eq{
		R:=\{A\subset\kappa\mid\exists\vec f:H_{\vec f}\subset A\},
	}

	where the $\vec f$'s range over finite sequences of functions as above; i.e. $f_0:[\kappa]^2\to 2$ and $f_{k+1}:[H_{f_k}]\to 2$ for $k<\omega$.	This is clearly a stationary class which satisfies that whenever $A\in R$ and $g:[A]^2\to 2$, we can find $H\in R$ which is homogeneous for $f$. Indeed, if we let $\vec f$ be such that $H_{\vec f}\subset A$, which exists as $A\in R$, then we can simply let $H:=H_{\vec f,g}$. This shows that $\kappa$ is completely ineffable.

	\qquad $(\Rightarrow)$: Now assume that $\kappa$ is completely ineffable and let $R$ be the corresponding stationary class. We show that $\kappa$ is $n$-Ramsey for all $n<\omega$ by induction, where we inductively make sure that the resulting strategies are coherent as well. Let player I in $\G_0(\kappa)$ play $\M_0$ and enumerate $\p(\kappa)\cap\M_0$ as $\vec A^0\bra{A^0_\alpha\mid\alpha<\kappa}$ such that $A^0_\xi\subset A^0_\zeta$ implies $\xi\leq\zeta$. For $\alpha<\kappa$ define sequences $r_\alpha:\alpha\to 2$ as $r_\alpha(\xi)=1$ iff $\alpha\in A^0_\xi$. Let $<_{\text{lex}}^\alpha$ be the lexicographical ordering on $^\alpha 2$. Define now a colouring $f:[\kappa]^2\to 2$ as
	\eq{
		f(\{\alpha,\beta\}):=\left\{\begin{array}{ll}0 & \text{if }r_{\min(\alpha,\beta)}<_{\text{lex}}^{\min(\alpha,\beta)}r_{\max(\alpha,\beta)}\restr\min(\alpha,\beta)\\ 1 & \text{otherwise}\end{array}\right.
	}

	Let $H_0\in R$ be homogeneous for $f$, using that $\kappa$ is completely ineffable. For $\alpha<\kappa$ consider now the sequence $\bra{r_\xi\restr\alpha\mid\xi\in H_0\land\xi>\alpha}$, which is of length $\kappa$ so there is an $\eta\in[\alpha,\kappa)$ satisfying that $r_\beta\restr\alpha=r_\gamma\restr\alpha$ for every $\beta,\gamma\in H_0$ with $\eta\leq\beta<\gamma$. Define $g:\kappa\to\kappa$ as $g(\alpha)$ being the least such $\eta$, which is then a continuous non-decreasing cofinal function, making the set of fixed points of $g$ club in $\kappa$ -- call this club $C$.

	\qquad Since $H_0$ is stationary we can pick some $\zeta\in C\cap H_0$. As $\zeta\in C$ we get $g(\zeta)=\zeta$, meaning that $r_\beta\restr\zeta=r_\gamma\restr\zeta$ holds for every $\beta,\gamma\in H_0$ with $\zeta\leq\beta<\gamma$. As $\zeta$ is also a member of $H_0$ we can let $\beta:=\zeta$, so that $r_\zeta=r_\gamma\restr\zeta$ holds for every $\gamma\in H_0$, $\gamma>\zeta$.	Now, by definition of $r_\alpha$ we get that for every $\alpha,\gamma\in H_0\cap C$ with $\alpha\leq\gamma$ and $\xi<\alpha$, $\alpha\in A^0_\xi$ iff $\gamma\in A^0_\xi$. Define thus the $\M_0$-measure $\mu_0$ on $\kappa$ as
	\eq{
		\mu_0(A^0_\xi)=1\quad&\text{iff}\quad(\forall\beta\in H_0\cap C)(\beta>\xi\to\beta\in A^0_\xi)\\
		&\text{iff}\quad(\exists\beta\in H_0\cap C)(\beta>\xi\land\beta\in A^0_\xi),
	}

	where the last equivalence is due to the above-mentioned property of $H_0\cap C$. Note that the choice of enumeration implies that $\mu_0$ is indeed a filter. Letting $\vec B=\bra{B_\alpha\mid\alpha<\kappa}$ be the $\mu_0$-positive part of $\vec A^0$, it is also simple to check that $H_0\cap C\subset\triangle\vec B$, making $\mu_0$ normal and hence also both $\M_0$-normal and good, showing that $\kappa$ is $0$-Ramsey.

	\qquad Assume now that $\kappa$ is $n$-Ramsey and let $\bra{\M_0,\mu_0,\hdots,\M_n,\mu_n,\M_{n+1}}$ be a partial play of $\G_{n+1}(\kappa)$. Again enumerate $\p(\kappa)\cap\M_{n+1}$ as $\vec A^{n+1}=\bra{A^{n+1}_\xi\mid\xi<\kappa}$, again satisfying that $\xi\leq\zeta$ whenever $A^{n+1}_\xi\subset A^{n+1}_\zeta$, but also such that given any $\xi<\kappa$ there are $\zeta,\zeta'\in(\xi,\kappa)$ satisfying that $A^{n+1}_\zeta\in\p(\kappa)\cap\M_n$ and $A^{n+1}_{\zeta'}\in(\p(\kappa)\cap\M_{n+1})-\M_n$. The plan now is to do the same thing as before, but we also have to check that the resulting measure extends the previous ones.

	\qquad Let $H_n\in R$ and $C$ be club in $\kappa$ such that $H_n\cap C\subset\triangle\mu_n$, which exist by our inductive assumption. For $\alpha<\kappa$ define $r_\alpha:\alpha\to 2$ as $r_\alpha(\xi)=1$ iff $\alpha\in A^{n+1}_\xi$, and define a colouring $f:[H_n]^2\to 2$ as
	\eq{
		f(\{\alpha,\beta\}):=\left\{\begin{array}{ll}0 & \text{if }r_{\min(\alpha,\beta)}<_{\text{lex}}^{\min(\alpha,\beta)}r_{\max(\alpha,\beta)}\restr\min(\alpha,\beta)\\ 1 & \text{otherwise}\end{array}\right.
	}

	As $H_n\in R$ there is an $H_{n+1}\in R$ homogeneous for $f$. Just as before, define $g:\kappa\to\kappa$ as $g(\alpha)$ being the least $\eta\in[\alpha,\kappa)$ such that $r_\beta\restr\alpha=r_\gamma\restr\alpha$ for every $\beta,\gamma\in H_{n+1}$ with $\eta\leq\beta<\gamma$, and let $D$ be the club of fixed points of $g$. As above we get that given any $\alpha,\gamma\in H_{n+1}\cap D$ with $\alpha\leq\gamma$ and $\xi<\alpha$, $\alpha\in A^{n+1}_\xi$ iff $\gamma\in A^{n+1}_\xi$. Define then the $\M_{n+1}$-measure $\mu_{n+1}$ on $\kappa$ as
	\eq{
		\mu_{n+1}(A^{n+1}_\xi)=1\quad&\text{iff}\quad(\forall\beta\in H_{n+1}\cap D\cap C)(\beta>\xi\to\beta\in A^{n+1}_\xi)\\
		&\text{iff}\quad(\exists\beta\in H_{n+1}\cap D\cap C)(\beta>\xi\land\beta\in A^{n+1}_\xi).
	}

	Then $H_{n+1}\cap D\cap C\subset\triangle\mu_{n+1}$, making $\mu_{n+1}$ normal, $\M_{n+1}$-normal and good, just as before. It remains to show that $\mu_n\subset\mu_{n+1}$. Let thus $A\in\mu_n$ be given, and say $A=A^{n+1}_\xi=A^n_\eta$, where $\vec A^n$ was the enumeration of $\p(\kappa)\cap\M_n$ used at the $n$'th stage. Then by definition of $\mu_n$ we get that for every $\beta\in H_n\cap C$ with $\beta>\eta$, $\beta\in A^n_\eta$. We need to show that
	\eq{
		(\exists\beta\in H_{n+1}\cap D\cap C)(\beta>\xi\land\beta\in A^{n+1}_\xi)
	}

	holds. But here we can simply pick a $\beta>\max(\xi,\eta)$ with $\beta\in H_{n+1}\cap D\cap C\subset H_n\cap C$. This shows that $\mu_n\subset\mu_{n+1}$, making $\kappa$ $(n{+}1)$-Ramsey and thus inductively also coherent ${<}\omega$-Ramsey.
}



\subsection{The countable case}

This section covers the (strategic) $\gamma$-Ramsey cardinals whenever $\gamma$ has countable cofinality. This case is special because, as mentioned in Section \ref{sect.settingthescene}, we cannot ensure that the final measure is countably complete and so the existence of winning strategies in the $\G_\gamma^\theta(\kappa)$ \textit{might} depend on $\theta$, in contrast with the uncountable cofinality case; see e.g. Question \ref{ques.ctbltheta}.\todo{Fix ref}

\subsection*{[Strategic] $\omega$-Ramsey cardinals}\todo{Remove the virtual definitions and basic results if they're redundant}

We now move to the strategic $\omega$-Ramsey cardinals and their relationship to the (non-strategic) $\omega$-Ramseys. For this we define a new addition to the family of \textit{virtual cardinals} from \cite{GitmanSchindler}, the \textit{virtually measurable cardinals}.

\defi{
	A cardinal $\kappa$ is \textbf{virtually measurable} if for every regular $\nu>\kappa$ there exists a transitive $M$ and a forcing $\mathbb P$ such that, in $V^{\mathbb P}$, there exists an elementary embedding $j:H_\nu^V\to M$ with $\crit j=\kappa$.
}

We'll need the following well-known lemmata; see Lemma 7.1 in \cite{HolySchlicht} and Lemma 3.1 in \cite{GitmanSchindler} for their proofs.

\qlemm[Ancient Kunen Lemma]{
  \label{lemm.Kunen}
  Let $M\models\zfc^-$ and $j:M\to N$ an elementary embedding with critical point $\kappa$ such that $\kappa+1\subset M\subset N$. Assume that $X\in M$ has $M$-cardinality $\kappa$. Then $j\restr X\in N$.
}

\qlemm[Absoluteness of embeddings on countable structures]{
  \label{lemm.absemb}
  Let $M$ be a countable first-order structure and $j:M\to N$ an elementary embedding. If $W$ is a transitive (set or class) model of (some sufficiently large fragment of) $\zfc$ such that $M$ is countable in $W$ and $N\in W$, then for any finite subset of $M$, $W$ has some elementary embedding $j^*:M\to N$, which agrees with $j$ on that subset. Moreover, if both $M$ and $N$ are transitive $\in$-structures and $j$ has a critical point, we can also assume that $\crit(j^*)=\crit(j)$.
}

\theo[Schindler-N.][theo.gengame]{
  Let $\kappa<\theta$ be regular cardinals. Then $\kappa$ is generically $\theta$-measurable iff player II has a winning strategy in $\C^\theta_\omega(\kappa)$.
}
\proof{
  $(\Leftarrow):$ Fix a winning strategy $\sigma$ for player II in $\C^\theta_\omega(\kappa)$. Let $g\subset\col(\omega,H^V_\theta)$ be $V$-generic and in $V[g]$ fix an elementary chain $\bra{\M_n\mid n<\omega}$ of weak $\kappa$-models $\M_n\prec H^V_\theta$ such that $H^V_\theta\subset\bigcup_{n<\omega}\M_n$, using that $\theta$ is regular and has countable cofinality in $V[g]$. Player II follows $\sigma$, resulting in a $H^V_\theta$-normal $H^V_\theta$-measure $\mu$ on $\kappa$.

  \qquad We claim that $\ult(H^V_\theta,\mu)$ is wellfounded, so assume not, witnessed by a sequence $\bra{g_n\mid n<\omega}$ of functions $g_n\colon\kappa\to\theta$ such that $g_n\in H^V_\theta$ and
  \eq{
    \{\alpha<\kappa\mid g_{n+1}(\alpha)<g_n(\alpha)\}\in\mu.
  }

  Now, in $V$, define a tree $\T$ of triples $(f,M_f,\mu_f)$ such that $f\colon\kappa\to\theta$, $M_f$ is a weak $\kappa$-model, $\mu_f$ is an $M_f$-measure on $\kappa$ and letting $f_0<_{\T}\cdots<_{\T}f_n=f$ be the $\T$-predecessors of $f$,
  \begin{itemize}
    \item $\bra{M_{f_0},\mu_{f_0},\hdots,M_{f_n},\mu_{f_n}}$ is a partial play of $\C^\theta_\omega(\kappa)$ in which player II follows $\sigma$; and
    \item $\{\alpha<\kappa\mid f_{k+1}(\alpha)<f_k(\alpha)\}\in\mu_{k+1}$ for every $k<n$.\\
  \end{itemize}

  Now the $g_n$'s induce a cofinal branch through $\T$ in $V[g]$, so by absoluteness of wellfoundedness there's a cofinal branch $b$ through $\T$ in $V$ as well. But $b$ now gives us a play of $C^\theta_\omega(\kappa)$ where player II is following $\sigma$ but player I wins, a contradiction. Thus $\ult(H^V_\theta,\mu)$ is wellfounded, so that the ultrapower embedding $\pi\colon H_\theta^V\to\ult(H_\theta^V,\mu)$ witnesses that $\kappa$ is generically $\theta$-measurable.

  \qquad $(\Rightarrow):$ Assume that $\kappa$ is generically $\theta$-measurable. Let $\mathbb P$ be a forcing $\dot\mu$ a $\mathbb P$-name for an $H_\theta^V$-normal $H_\theta^V$-measure on $\kappa$ and $\dot\pi$ a $\mathbb P$-name for the associated ultrapower embedding. Define a strategy for player II in $\C_\omega^\theta(\kappa)$ as follows: Whenever player I plays $\M_n$ then fix some $\mathbb P$-condition $p_n$ such that, letting $\bra{f_i^n\mid i<k}$ enumerate all functions in $\M_n$ with domain $\kappa$,
  \eq{
    p_n\forces\godel{\check\mu\cap\M_n=\check\mu_n\cap\forall i<\check k\colon\dot\pi(\check f_i^n)(\check\kappa)=\check\alpha_i^n},
  }

  with $\mu_n,\alpha_i^n\in V$. Note here that we can ensure $\mu_n\in V$ because it's finite. Also, ensure that the $p_n$'s are $\leq$-decreasing. Assume now that $\ult(\M_\omega,\mu_\omega)$ is illfounded, witnessed by functions $g_n\in{^\kappa\M_\omega}\cap\M_\omega$ for $n<\omega$. Then $g_n=f_{i_n}^{k_n}$ for some $k_n,i_n<\omega$, and hence $p_{k_{n+1}}\forces\godel{\check\alpha_{i_{n+1}}^{k_{n+1}}<\check\alpha_{i_n}^{k_n}}$ for every $n<\omega$, so in $V$ we get an $\omega$-sequence of strictly decreasing ordinals, $\contr$.
}

Here's a near-analogous result for the $\G^\theta_\omega(\kappa)$ game from \cite{NielsenWelch}, with a proof added for completeness.

\theo[Schindler-N.]{
  Let $\kappa<\theta$ be regular cardinals. If $\kappa$ is virtually $\theta$-prestrong then player II has a winning strategy in $\G^\theta_\omega(\kappa)$, and if player II has a winning strategy in $\G_\omega^\theta(\kappa)$ then $\kappa$ is generically $\theta$-power-measurable. In particular, $\G^\theta_\omega(\kappa)^L\sim\C^\theta_\omega(\kappa)^L$.
}

\proof{
  The second statement is exactly like the $(\Leftarrow)$ direction in the previous theorem, so we show the first statement. Assume $\kappa$ is virtually $\theta$-prestrong and fix a regular $\theta>\kappa$, a transitive $\M\in V$, a poset $\mathbb P$ and, in $V^{\mathbb P}$, an elementary embedding $\pi\colon H_\theta^V\to\M$ with $\crit\pi=\kappa$. Fix a name $\dot\mu$ and a $\mathbb P$-condition $p$ such that
  \eq{
    p\forces\godel{\text{$\dot\mu$ is a weakly amenable $\check H_\theta$-normal $\check H_\theta$-measure with a wellfounded ultrapower}}.
  }

  We now define a strategy $\sigma$ for player II in $\G^\theta_\omega(\kappa)$ as follows. Whenever player I plays a weak $\kappa$-model $\M_n\prec H_\theta^V$, player II fixes $p_n\in\mathbb P$, an $\M_n$-measure $\mu_n$ and a function $\pi_n\colon\M_n\to\pi(\M_n)$ such that $p_0\leq p$, $p_n\leq p_k$ for every $k\leq n$ and that
  \eq{
    p_n\forces\godel{\dot\mu\cap\check\M_n=\check\mu_n\cap\check\mu_n=\dot\mu\restr\check\M_n}.\tag*{$(1)$}
  }

  Note that by the Ancient Kunen Lemma \ref{lemm.kunen} we get that $\pi\restr\M_n\in\M\subset V$, so such $\pi_n$ always exist in $V$. The $\mu_n$'s also always exist in $V$, by weak amenability of $\mu$. Player II responds to $\M_n$ with $\mu_n$. It's clear that the $\mu_n$'s are legal moves for player II, so it remains to show that $\mu_\omega:=\bigcup_{n<\omega}\mu_n$ has a wellfounded ultrapower. Assume it hasn't, so that we have a sequence $\bra{g_n\mid n<\omega}$ of functions $g_n\colon\kappa\to\M_\omega:=\bigcup_{n<\omega}\M_n$ such that $g_n\in\M_\omega$ and
  \eq{
    X_{n+1}:=\{\alpha<\kappa\mid g_{n+1}(\alpha)<g_n(\alpha)\}\in\mu_\omega\tag*{$(2)$}
  }

  for every $n<\omega$. Without loss of generality we can assume that $g_n,X_n\in\M_n$. Then $(2)$ implies that $p_{n+1}\forces\godel{\dot\pi(\check g_{n+1})(\check\kappa)<\dot\pi(\check g_n)(\check\kappa)}$, but by $(1)$ this also means that
  \eq{
    p_{n+1}\forces\godel{\check\pi_{n+1}(\check g_{n+1})(\check\kappa)<\check\pi_n(\check g_n)(\check\kappa)},
  }

  so defining, in $V$, the ordinals $\alpha_n:=\pi_n(g_n)(\kappa)$, $(3)$ implies that $\alpha_{n+1}<\alpha_n$ for all $n<\omega$, $\contr$. So $\mu_\omega$ has a wellfounded ultrapower, making $\sigma$ a winning strategy.
}

\ques{
  If $\kappa$ is generically $\theta$-power-measurable, does player II then have a winning strategy in $\G^\theta_\omega(\kappa)$?
}

We get the following immediate corollary.

\qcoro[N.-Schindler]{
	\label{coro.strategic}
  Strategic $\omega$-Ramseys are downwards absolute to $L$, and the existence of a strategic $\omega$-Ramsey cardinal is equiconsistent with the existence of a virtually measurable cardinal. Further, in $L$ the two notions are equivalent.
}

Note also that the proof of Theorem \ref{theo.virtstrat} shows that whenever $\kappa$ is strategic $\omega$-Ramsey then for every regular $\nu>\kappa$ there's a generic extension in which there exists a weakly amenable $H_\nu^V$-normal $H_\nu$-measure on $\kappa$.

\qquad We end this section with a result showing precisely where in the large cardinal hierarchy the strategic $\omega$-Ramsey cardinals and $\omega$-Ramsey cardinals lie, namely that strategic $\omega$-Ramseys are equiconsistent with \textit{remarkables} and $\omega$-Ramseys are strictly below. Theorem 4.8 of \cite{Ramsey2} showed that 2-iterables are limits of remarkables, and our Propositions \ref{prop.tildegame} and \ref{prop.ramseyit} shows that $\omega$-Ramseys are limits of 1-iterables, so that the strategic $\omega$-Ramseys and the $\omega$-Ramseys both lie strictly between the 2-iterables and 1-iterables. It was shown in \cite{HolySchlicht} that $\omega$-Ramseys are consistent with $V=L$. Remarkable cardinals were introduced by \cite{remarkable}, and \cite{GitmanSchindler} showed the following two equivalent formulations.

\defi{
	\label{defi.remarkable}
	A cardinal $\kappa$ is \textbf{remarkable} if one of the two equivalent properties hold:
	\begin{enumerate}
		\item For all $\lambda>\kappa$ there exist $\nu>\lambda$, a transitive set $M$ with $H_\lambda^V\subset M$ and a forcing poset $\mathbb P$, such that in $V^{\mathbb P}$ there's an elementary embedding $\pi:H_\nu^V\to M$ with critical point $\kappa$ and $\pi(\kappa)>\lambda$;
		\item For all $\lambda>\kappa$ there exist $\nu>\lambda$, a transitive set $M$ with ${^\lambda}M\subset M$ and a forcing poset $\mathbb P$, such that in $V^{\mathbb P}$ there's an elementary embedding $\pi:H_\nu^V\to M$ with critical point $\kappa$ and $\pi(\kappa)>\lambda$.
	\end{enumerate}
}

\theo[N.]{
	\label{theo.remarkable}
	Let $\kappa$ be a virtually measurable cardinal. Then either $\kappa$ is either remarkable in $L$ or $L_\kappa\models\godel{\text{there is a proper class of virtually measurables}}$. In particular, the two notions are equiconsistent.
}
\proof{
	Virtually measurables are downwards absolute to $L$ by Lemma \ref{lemm.absemb}, so we may assume $V=L$. Assume $\kappa$ is not remarkable. This means that there exists some $\lambda>\kappa$ such that for every $\nu>\lambda$, transitive $M$ with $H_\lambda^V\subset M$ and forcing poset $\mathbb P$ it holds that, in $V^{\mathbb P}$, there's no elementary embedding $\pi:H_\nu^V\to M$ with $\crit\pi=\kappa$ and $\pi(\kappa)>\lambda$.
	
	\qquad Fix $\nu:=\lambda^+$ and use that $\kappa$ is virtually $\nu$-measurable to fix a transitive $M$ and a forcing poset $\mathbb P$ such that, in $V^{\mathbb P}$, there's an elementary $\pi:H_\nu^V\to M$. Note that because $M\models V=L$ and $M$ is transitive, $M=L_\alpha$ for some $\alpha\geq\nu$, so that $H_\nu^V=L_\nu\subset M$. This means that $\pi(\kappa)\leq\lambda<\nu$ since we're assuming that $\kappa$ isn't remarkable. Then by restricting the generic embedding to $H_\kappa^V$ we get that $H_\kappa^V\prec H_{\pi(\kappa)}^M=H_{\pi(\kappa)}^V$, using that $\pi(\kappa)<\nu$ and $H_\nu^V=H_\nu^M$ by the above.
	
	\qquad Note that $\pi(\kappa)$ is a cardinal in $H_\nu^V$ since $\pi(\kappa)<\nu$, and as $H_\nu^V\prec_1 V$ we get that $\pi(\kappa)$ \textit{is} a cardinal. But then, again using that $H_{\pi(\kappa)}\prec_1 V$, $\kappa$ is virtually measurable in $H_{\pi(\kappa)}^V$ since being virtually measurable is $\Pi_2$. This means that for every $\xi<\kappa$ it holds that
	\eq{
		H_{\pi(\kappa)}^V\models\exists\alpha>\xi:\godel{\text{$\alpha$ is virtually measurable}},
	}

	implying that $H_\kappa^V\models\godel{\text{There is a proper class of virtually measurables}}$.
}

Now Theorem \ref{theo.remarkable} and Corollary \ref{coro.strategic} yield the following immediate corollary.

\qcoro[N.-Schindler]{
  Let $\kappa$ be strategic $\omega$-Ramsey. Then either $\kappa$ is remarkable in $L$ or otherwise
  \eq{
    L_\kappa\models\godel{\text{there is a proper class of strategic $\omega$-Ramseys}}. 
  }
    
  In particular, the two notions are equiconsistent.
}

Now, using these results we show that the strategic $\omega$-Ramseys have strictly stronger consistency strength than the $\omega$-Ramseys.

\theo[N.]{
	\label{theo.remlimram}
	Remarkable cardinals are strategic $\omega$-Ramsey limits of $\omega$-Ramsey cardinals.
}
\proof{
	Let $\kappa$ be remarkable. Using property $(ii)$ in the definition of remarkability above we can find a transitive $M$ closed under $2^\kappa$-sequences and a generic elementary embedding $\pi:H_\nu^V\to M$ for some $\nu>2^\kappa$. We will show that $\kappa$ is $\omega$-Ramsey in $M$. Note that remarkables are clearly virtually measurable, and thus by Theorem \ref{theo.virtstrat} also strategic $\omega$-Ramsey; let $\tau_\theta$ be the winning strategy for player II in $\G_\omega^\theta(\kappa)$ for all regular $\theta>\kappa$.

	\qquad In $M$ we fix some regular $\theta>\kappa$ and let $\sigma$ be some strategy for player I in $\G_\omega^\theta(\kappa)^M$. Since $M$ is closed under $2^\kappa$-sequences it means that $\p(\p(\kappa))\subset M$ and thus that $M$ contains all possible filters on $\kappa$. We let player II follow $\tau$, which produces a play $\sigma*\tau$ in which player II wins. But all player II's moves are in $\p(\p(\kappa))$ and hence in $M$, and as $M$ is furthermore closed under $\omega$-sequences, $\sigma*\tau\in M$. This means that $M$ sees that $\sigma$ is not winning, so $\kappa$ is $\omega$-Ramsey in $M$.
	
	\qquad This also implies that $\kappa$ is a limit of $\omega$-Ramseys in $H_\nu$. But as $\kappa$ is remarkable it holds that $H_\kappa\prec_2 V$, in analogy with the same property for strongs and supercompacts, and as being $\omega$-Ramsey is a $\Pi_2$-notion this means that $\kappa$ \textit{is} a limit of $\omega$-Ramseys.
}

This immediately yields the following corollary.

\coro[N.-Schindler]{
	If $\kappa$ is a strategic $\omega$-Ramsey cardinal then
	\eq{
		L_\kappa\models\godel{\text{there is a proper class of $\omega$-Ramseys}}.\tag*{$\dashv$}
	}
}

\subsection*{When we have a winning strategy}

\theo[Schindler-N.][theo.gengame]{
  Let $\kappa<\theta$ be regular cardinals. Then $\kappa$ is generically $\theta$-measurable iff player II has a winning strategy in $\C^\theta_\omega(\kappa)$.
}
\proof{
  $(\Leftarrow):$ Fix a winning strategy $\sigma$ for player II in $\C^\theta_\omega(\kappa)$. Let $g\subset\col(\omega,H^V_\theta)$ be $V$-generic and in $V[g]$ fix an elementary chain $\bra{\M_n\mid n<\omega}$ of weak $\kappa$-models $\M_n\prec H^V_\theta$ such that $H^V_\theta\subset\bigcup_{n<\omega}\M_n$, using that $\theta$ is regular and has countable cofinality in $V[g]$. Player II follows $\sigma$, resulting in a $H^V_\theta$-normal $H^V_\theta$-measure $\mu$ on $\kappa$.

  \qquad We claim that $\ult(H^V_\theta,\mu)$ is wellfounded, so assume not, witnessed by a sequence $\bra{g_n\mid n<\omega}$ of functions $g_n\colon\kappa\to\theta$ such that $g_n\in H^V_\theta$ and
  \eq{
    \{\alpha<\kappa\mid g_{n+1}(\alpha)<g_n(\alpha)\}\in\mu.
  }

  Now, in $V$, define a tree $\T$ of triples $(f,M_f,\mu_f)$ such that $f\colon\kappa\to\theta$, $M_f$ is a weak $\kappa$-model, $\mu_f$ is an $M_f$-measure on $\kappa$ and letting $f_0<_{\T}\cdots<_{\T}f_n=f$ be the $\T$-predecessors of $f$,
  \begin{itemize}
    \item $\bra{M_{f_0},\mu_{f_0},\hdots,M_{f_n},\mu_{f_n}}$ is a partial play of $\C^\theta_\omega(\kappa)$ in which player II follows $\sigma$; and
    \item $\{\alpha<\kappa\mid f_{k+1}(\alpha)<f_k(\alpha)\}\in\mu_{k+1}$ for every $k<n$.\\
  \end{itemize}

  Now the $g_n$'s induce a cofinal branch through $\T$ in $V[g]$, so by absoluteness of wellfoundedness there's a cofinal branch $b$ through $\T$ in $V$ as well. But $b$ now gives us a play of $C^\theta_\omega(\kappa)$ where player II is following $\sigma$ but player I wins, a contradiction. Thus $\ult(H^V_\theta,\mu)$ is wellfounded, so that the ultrapower embedding $\pi\colon H_\theta^V\to\ult(H_\theta^V,\mu)$ witnesses that $\kappa$ is generically $\theta$-measurable.

  \qquad $(\Rightarrow):$ Assume that $\kappa$ is generically $\theta$-measurable. Let $\mathbb P$ be a forcing $\dot\mu$ a $\mathbb P$-name for an $H_\theta^V$-normal $H_\theta^V$-measure on $\kappa$ and $\dot\pi$ a $\mathbb P$-name for the associated ultrapower embedding. Define a strategy for player II in $\C_\omega^\theta(\kappa)$ as follows: Whenever player I plays $\M_n$ then fix some $\mathbb P$-condition $p_n$ such that, letting $\bra{f_i^n\mid i<k}$ enumerate all functions in $\M_n$ with domain $\kappa$,
  \eq{
    p_n\forces\godel{\check\mu\cap\M_n=\check\mu_n\cap\forall i<\check k\colon\dot\pi(\check f_i^n)(\check\kappa)=\check\alpha_i^n},
  }

  with $\mu_n,\alpha_i^n\in V$. Note here that we can ensure $\mu_n\in V$ because it's finite. Also, ensure that the $p_n$'s are $\leq$-decreasing. Assume now that $\ult(\M_\omega,\mu_\omega)$ is illfounded, witnessed by functions $g_n\in{^\kappa\M_\omega}\cap\M_\omega$ for $n<\omega$. Then $g_n=f_{i_n}^{k_n}$ for some $k_n,i_n<\omega$, and hence $p_{k_{n+1}}\forces\godel{\check\alpha_{i_{n+1}}^{k_{n+1}}<\check\alpha_{i_n}^{k_n}}$ for every $n<\omega$, so in $V$ we get an $\omega$-sequence of strictly decreasing ordinals, $\contr$.
}

Here's a near-analogous result for the $\G^\theta_\omega(\kappa)$ game from \cite{NielsenWelch}, with a proof added for completeness.

\theo[Schindler-N.]{
  Let $\kappa<\theta$ be regular cardinals. If $\kappa$ is virtually $\theta$-prestrong then player II has a winning strategy in $\G^\theta_\omega(\kappa)$, and if player II has a winning strategy in $\G_\omega^\theta(\kappa)$ then $\kappa$ is generically $\theta$-power-measurable. In particular, $\G^\theta_\omega(\kappa)^L\sim\C^\theta_\omega(\kappa)^L$.
}

\proof{
  The second statement is exactly like the $(\Leftarrow)$ direction in the previous theorem, so we show the first statement. Assume $\kappa$ is virtually $\theta$-prestrong and fix a regular $\theta>\kappa$, a transitive $\M\in V$, a poset $\mathbb P$ and, in $V^{\mathbb P}$, an elementary embedding $\pi\colon H_\theta^V\to\M$ with $\crit\pi=\kappa$. Fix a name $\dot\mu$ and a $\mathbb P$-condition $p$ such that
  \eq{
    p\forces\godel{\text{$\dot\mu$ is a weakly amenable $\check H_\theta$-normal $\check H_\theta$-measure with a wellfounded ultrapower}}.
  }

  We now define a strategy $\sigma$ for player II in $\G^\theta_\omega(\kappa)$ as follows. Whenever player I plays a weak $\kappa$-model $\M_n\prec H_\theta^V$, player II fixes $p_n\in\mathbb P$, an $\M_n$-measure $\mu_n$ and a function $\pi_n\colon\M_n\to\pi(\M_n)$ such that $p_0\leq p$, $p_n\leq p_k$ for every $k\leq n$ and that
  \eq{
    p_n\forces\godel{\dot\mu\cap\check\M_n=\check\mu_n\cap\check\mu_n=\dot\mu\restr\check\M_n}.\tag*{$(1)$}
  }

  Note that by the Ancient Kunen Lemma \ref{lemm.kunen} we get that $\pi\restr\M_n\in\M\subset V$, so such $\pi_n$ always exist in $V$. The $\mu_n$'s also always exist in $V$, by weak amenability of $\mu$. Player II responds to $\M_n$ with $\mu_n$. It's clear that the $\mu_n$'s are legal moves for player II, so it remains to show that $\mu_\omega:=\bigcup_{n<\omega}\mu_n$ has a wellfounded ultrapower. Assume it hasn't, so that we have a sequence $\bra{g_n\mid n<\omega}$ of functions $g_n\colon\kappa\to\M_\omega:=\bigcup_{n<\omega}\M_n$ such that $g_n\in\M_\omega$ and
  \eq{
    X_{n+1}:=\{\alpha<\kappa\mid g_{n+1}(\alpha)<g_n(\alpha)\}\in\mu_\omega\tag*{$(2)$}
  }

  for every $n<\omega$. Without loss of generality we can assume that $g_n,X_n\in\M_n$. Then $(2)$ implies that $p_{n+1}\forces\godel{\dot\pi(\check g_{n+1})(\check\kappa)<\dot\pi(\check g_n)(\check\kappa)}$, but by $(1)$ this also means that
  \eq{
    p_{n+1}\forces\godel{\check\pi_{n+1}(\check g_{n+1})(\check\kappa)<\check\pi_n(\check g_n)(\check\kappa)},
  }

  so defining, in $V$, the ordinals $\alpha_n:=\pi_n(g_n)(\kappa)$, $(3)$ implies that $\alpha_{n+1}<\alpha_n$ for all $n<\omega$, $\contr$. So $\mu_\omega$ has a wellfounded ultrapower, making $\sigma$ a winning strategy.
}

\ques{
  If $\kappa$ is generically $\theta$-power-measurable, does player II then have a winning strategy in $\G^\theta_\omega(\kappa)$?
}


\pagebreak
\section{Ideals}

\defi{
	A poset property\footnote{Examples of these are having the $\kappa$-chain condition, being $\kappa$-closed, $\kappa$-distributive, $\kappa$-Knaster, $\kappa$-sized and so on.} $\Phi(\kappa)$ is \textbf{ideal-absolute} if whenever $\kappa$ satisfies that there's a $\Phi(\kappa)$ forcing poset $\mathbb P$ such that, in $V^{\mathbb P}$, there's a $V$-normal $V$-measure $\mu$ on $\kappa$, then there's an ideal $I$ on $\kappa$ such that $\p(\kappa)/I$ is forcing equivalent to a forcing satisfying $\Phi(v)$.
}

Note that this is \textit{almost} saying that $\Phi(\kappa)$ ideally measurables are equivalent to $\Phi(\kappa)$ generically $\infty$-measurables, but the only difference is that these definitions require well-foundedness of the above $M$.

\qquad Also note that $\omega$-distributive generically $\theta_0$-measurable cardinals are equivalent to $\omega$-distributive generically $\theta_1$-measurable cardinals for all regular $\theta_0,\theta_1\in\infty\cup\{\infty\}$ since wellfoundedness becomes automatic, so in this case we will simply write ``$\omega$-distributive generically measurable''.

\qquad Note that the ideally measurables aren't equiconsistent with the generically- and virtually measurables, since the ideally measurable cardinals are ideally $\infty$-measurable \todo{Add proof?} and are therefore equiconsistent with a measurable cardinal. Because of this proposition we will refrain from using the ``ideally $\infty$-measurable'' terminology and only use ``ideally measurable'' from now on.

\qquad We \textit{do} get an equiconsistency at the critical level though, as Theorem 2.11 of \cite{FerberGitik} shows that if $\kappa$ is generically critical then it's ideally critical in $L^{\col(\omega,{<}\kappa)}$.


\defi{
	Let $\kappa$ be a regular cardinal, $\mathbb P$ a poset and $\dot\mu$ a $\mathbb P$-name for a $V$-normal $V$-measure on $\kappa$. Then the \textbf{induced ideal} is
		\eq{
			\I(\mathbb P,\dot\mu):=\{X\subset\kappa\mid\norm{\check X\in\dot\mu}_{\B(\mathbb P)}=0\},
		}

		where $\B(\mathbb P)$ is the boolean completion of $\mathbb P$.
}

Note that if the generic measure $\mu$ is furthermore $V$-normal then $\I(\mathbb P,\dot\mu)$ is also normal.


\subsection{$\kappa^+$-chain condition\todo{Other chain conditions?}}

\theo[Folklore]{
	``The $\kappa^+$-chain condition'' is ideal-absolute.
}
\proof{
	Assume $\mathbb P$ has the $\kappa^+$-chain condition such that there's a $\mathbb P$-name $\dot\mu$ for a $V$-normal $V$-measure on $\kappa$. Let $I:=\I(\mathbb P,\dot\mu)$ --- we will show that $\p(\kappa)/I$ has the $\kappa^+$-chain condition. Assume not and let $\bra{X_\alpha\mid\alpha<\kappa^+}$ be an antichain of $\p(\kappa)/I$, which by normality of $I$ we may assume is pairwise almost disjoint. But this then makes $\bra{\norm{\check X_\alpha\in\dot\mu}_{\B(\mathbb P)}\mid\alpha<\kappa^+}$ an antichain of $\mathbb P$ of size $\kappa^+$, $\contr$.
}


\subsection{${<}\lambda$-distributivity}

Recall that an ideal $I$ on some $\kappa$ is $\omega$-distributive if and only if it's precipitous\footnote{See \cite{Precipitous} and \cite{Foreman}.}, so that carrying an $\omega$-distributive ideal coincides with our definition of \textit{ideally measurable}.

\theo[N.]{
	``${<}\lambda$-distributivity'' is ideal-absolute for all regular $\lambda\in[\omega,\kappa^+]$.
}
\proof{
	Assume that $\mathbb P$ is a ${<}\lambda$-distributive forcing such that there exists a $\mathbb P$-name $\dot\mu$ for a $V$-normal $V$-measure on $\kappa$. Let $I:=\I(\mathbb P,\dot\mu)$ --- we'll show that $\p(\kappa)/I$ is ${<}\lambda$-distributive. Let $\T\subset(\p(\kappa)/I)^{<\lambda}$ be an unrooted tree \todo{Do this in terms of $\prec$-chains of antichains instead.} of height ${<}\lambda$ such that every level $\T_\alpha$ is a maximal antichain. We have to show that there's a maximal antichain $\A$ consisting of limit points of branches of $\T$. Now define a corresponding tree $\T^*\subset\mathbb P^{<\lambda}$ as
	\eq{
		\T^*_\alpha:=\{\norm{\check X\in\dot\mu}_{\B(\mathbb P)}\mid X\in\T_\alpha\}.
	}

	\qquad Note that every level $\T^*_\alpha$ is an antichain in $\mathbb P$. They're also maximal, because if $p\in\mathbb P$ was incompatible with every condition in $\T^*_\alpha$ then, letting $X:=\bigcap\T_\alpha$, we have that $p$ is compatible with $\norm{\check X\in\dot\mu}_{\B(\mathbb P)}$, so that $X\in I^+$. But $X$ is incompatible with everything in $\T_\alpha$, contradicting that $\T_\alpha$ is maximal.

	\qquad By ${<}\lambda$-distributivity of $\mathbb P$ we get an antichain $\A^*$ consisting of limit points of branches of $\T^*$. But note that for every $p\in\A^*$ it holds that $p\leq\norm{\Delta b_p\in\dot\mu}_{\B(\mathbb P)}$ with $b_p$ being the branch of $\T^*$ with limit $p$,\footnote{Here we're using that all branches have length ${<}\kappa^+$, by choice of $\lambda$.} so that $\Delta b_p\in I^+$. Now $\A:=\{\Delta b_p\mid p\in\A^*\}$ gives us a maximal antichain consisting of limit points of branches of $\T$.
}

\ques{
	Is ``$\omega$-distributive $(\kappa,\kappa)$-distributive'' ideal-absolute? Does it correspond to generically power-measurables?
}


\subsection{$(\kappa,\kappa)$-distributivity \& ${<}\lambda$-closure}

In this section we will prove a slightly stronger version of the following unpublished result by Foreman:

\theo[Foreman]{
  Let $\kappa$ be a regular cardinal such that $2^\kappa = \kappa^+$, and let $\lambda\leq\kappa^+$ be an infinite successor cardinal. If player II has a winning strategy in $\G_\lambda(\kappa)$ then $\kappa$ carries a $\kappa$-complete normal precipitous ideal $\I$ such that $\p(\kappa)/\I$ has a dense ${<}\lambda$-closed subset of size $\kappa^+$.
}

\theo[Foreman-N.]{
  \label{theo.hopelessideal}
	Let $\kappa$ be a regular cardinal and $\lambda\leq\kappa^+$ be regular infinite. If player II has a winning strategy in $\G_\lambda^-(\kappa)$ then $\kappa$ carries a $\kappa$-complete normal ideal $\I$ such that $\p(\kappa)/\I$ is $(\kappa,\kappa)$-distributive and has a dense ${<}\lambda$-closed subset of size $\kappa^+$.
}

Before we start the proof, let us note that the only difference between the two theorems is that we are requiring neither $2^\kappa=\kappa^+$ nor that $\lambda$ is a successor cardinal. The proof strategy is similar to the original proof, but with some more technical details to ensure these strengthenings.\\

\proof{
  Set $\mathbb P:=\text{Add}(\kappa^+,1)$ if $2^\kappa>\kappa^+$ and $\mathbb P:=\{\emptyset\}$ otherwise. If $\kappa$ is measurable then the dual ideal to the measure on $\kappa$ satisfies all of the wanted properties, so assume that $\kappa$ is not measurable.	Fix a wellordering $<_{\kappa^+}$ of $H_{\kappa^+}$ and a $\mathbb P$-name $\pi$ for a sequence $\bra{\N_\gamma\mid\gamma<\kappa^+}\in V^{\mathbb P}$ such that
\begin{itemize}
	\item $\N_\gamma\in V$ for every $\gamma<\kappa^+$;
  \item $\N_{\gamma+1}\prec H_{\kappa^+}^V$ is a $\kappa$-model for every $\gamma<\kappa^+$;
  \item $\N_\delta=\bigcup_{\gamma<\delta}\N_\gamma$ for limit ordinals $\delta<\kappa^+$;
  \item $\N_\gamma\cup\{\N_\gamma\}\subset\N_\beta$ for $\gamma<\beta<\kappa^+$;
	\item $\p(\kappa)^V\subset\bigcup_{\gamma<\kappa^+}\N_\gamma$.\\
\end{itemize}

Define now the auxilliary game $\G(\kappa)$ of length $\lambda$ as follows.
\game{\alpha_0}{p_0,\M_0,\mu_0,Y_0}{\alpha_1}{p_1,\M_1,\mu_1,Y_1}{\cdots}{\cdots}{}{}

Here $\bra{\alpha_\gamma\mid\gamma<\lambda}$ is an increasing continuous sequence of ordinals bounded in $\kappa^+$, $\vec p_\gamma$ is a decreasing sequence of $\mathbb P$-conditions satisfying that
	\eq{
		&p_\gamma\forces\godel{\check\M_\gamma=\pi(\check\alpha_\gamma)\land\text{$\check\mu_\gamma$ is a $\check\M_\gamma$-normal $\check\M_\gamma$-measure on $\check\kappa$}}
	}

	such that $Y_\gamma=\Delta_{\xi<\kappa} X^{\mu_\gamma}_\xi$, where $\vec X^{\mu_\gamma}_\xi\in H_{\kappa^+}^V$ is the $<_{\kappa^+}$-least enumeration of $\mu_\gamma$.\footnote{We use that $\mathbb P$ is $\kappa$-closed to get the $p_\gamma$'s as well as to ensure that $\M_\gamma,\mu_\gamma\in V$.} We require that the $\mu_\gamma$'s are $\subset$-increasing, and player II wins iff she can continue playing throughout all $\lambda$ rounds. Let $\mu_\lambda:=\bigcup_{\xi<\lambda}\mu_\xi$ be the \textbf{final measure} of the play.
	
	\qquad To every limit ordinal $\eta<\kappa^+$ define the \textbf{restricted auxilliary game} $\G(\kappa)\restr\eta$ in which player I is only allowed to play ordinals ${<}\eta$. Note that a strategy $\tau$ for player II is winning in $\G(\kappa)$ if and only if it's winning in $\G(\kappa)\restr\eta$ for all $\eta<\kappa^+$, simply because all sequences of ordinals played by player I are bounded in $\kappa^+$.
	
	\qquad Note that $\mu_\lambda$ is precisely the tail measure on $\kappa$ defined by the $Y_\gamma$'s; i.e. that $X\in\mu_\lambda$ iff there exists a $\delta<\lambda$ such that $\abs{Y_\delta-X}<\kappa$. From this it's simple to see that $\G(\kappa)$ is equivalent to $\G_\lambda^-(\kappa)$, so player II has a winning strategy $\tau_0$ in $\G(\kappa)$. 
	
	\qquad For any winning strategy $\tau$ in $\G(\kappa)\restr\eta$ and to every partial play $p$ of $\G(\kappa)\restr\eta$ consistent with $\tau$, define the associated \textbf{hopeless ideal}\footnote{This terminology is due to Matt Foreman.}
	\eq{
		I_p^\tau\restr\eta:=\{X\subset\kappa\mid\ &\text{For every play $\vec\alpha_\gamma*\tau$ extending $p$ in $\G(\kappa)\restr\eta$,}\\ &\text{$X$ is \textit{not} in the final measure}\}
	}

	\clai{
		\label{clai.hopelessideal}
		Every hopeless ideal $I_p^\tau\restr\eta$ is normal and $(\kappa,\kappa)$-distributive.
	}

	\cproof{
		For normality, if $\bra{Z_\gamma\mid\gamma<\kappa}$ is a sequence of elements of $I_p^\tau$ such that $Z:=\nabla_\gamma Z_\gamma$ is $I_p^\tau$-positive, then there exists a play of $\G(\kappa)\restr\eta$ in which player II follows $\tau$ such that $Z$ lies in the final measure. If we let player I play sufficiently large ordinals in $\G(\kappa)\restr\eta$ we may assume that $\bra{Z_\gamma\mid\gamma<\kappa}$ is a subset and an element of the final model as well, meaning that one of the $Z_\gamma$'s also lies in the final measure, $\contr$.

		\qquad We now show $(\kappa,\kappa)$-distributivity. Let $\U\subset\p(\kappa)/I_p^\tau$ be an unrooted tree of height $\kappa$ such that every level $\U_\alpha$ is a maximal antichain of size $\leq\kappa$. We have to show that there's a maximal antichain $\mathcal A$ consisting of limit points of branches of $\U$. Pick $X\in\U$ and let $p$ be a play of $\G(\kappa)\restr\eta$ consistent with $\tau$ with limit model $\M$ and limit measure $\mu$, such that $X\in\mu$.
		
		\qquad By letting player I in $p$ play sufficiently large ordinals, we may assume that $\U\subset\M$, using that $\abs{\U}\leq\kappa$, and also that $b_X:=\U\cap\mu\in\M$. This means that $d_X:=\Delta b_X\in\p(\kappa)/I_p^\tau$ is a limit point of the branch $b_X$ through $\U$, so that $\mathcal A:=\{d_X\mid X\in\U\}$ is a maximal antichain of limit points of branches of $\U$, making $\p(\kappa)/I_p^\tau$ $(\kappa,\kappa)$-distributive.
	}

	Fix some limit ordinal $\eta<\kappa^+$. We will recursively construct a tree $\T^\eta$ of height $\lambda$ which consists of subsets $X\subset\kappa$, ordered by reverse inclusion. During the construction of the tree we will inductively maintain the following properties of $\T^\eta\restr\alpha$ for $\alpha\leq\lambda$:\\

	\begin{itemize}
		\item \textsc{Tree strategy}: For every $\gamma<\alpha$ there is a winning strategy $\tau^\eta_\gamma$ for player II in $\G(\kappa)\restr\eta$ such that for every $\beta<\gamma$, the $\beta$'th move by $\tau^\eta_\gamma$ is an element of $\T^\eta_\beta$ and $\tau^\eta_\gamma$ is consistent with $\tau^\eta_\beta$ for the first $\beta$-many rounds.
		\item \textsc{Unique pre-history}: Given any $\beta<\alpha$ and $Y\in\T^\eta_\beta$ there's a unique partial play $p$ of $\G(\kappa)\restr\eta$ consistent with $\tau^\eta_\beta$ ending with $Y$ --- we define $I_Y^\tau:=I_p^\tau$ for $\tau$ being any winning strategy for player II in $\G(\kappa)\restr\eta$ satisfying that $p$ is consistent with $\tau^\eta_\beta$.
		\item \textsc{Cofinally many responds}: Let $\beta+1<\alpha$ and $Y\in\T^\eta_\beta$, and set $p$ to be the unique partial play of $\G(\kappa)\restr\eta$ given by the unique pre-history of $Y$. Then the $\T^\eta$-successors of $Y$ consists of player II's $\tau^\eta_\beta$-responds to $\tau^\eta_\beta$-partial plays extending $p$ such that player I's last move in these partial plays are cofinal in $\eta$.\footnote{The reason why we're dealing with the \textit{restricted} auxilliary games is to achieve this property.}
		\item \textsc{Positivity}: If $\beta<\alpha$ and $Y\in\T^\eta_\beta$ then $Y$ is $I_X^{\tau^\eta_\gamma}$-positive for every $\gamma<\beta$ and every $X\in\T^\eta\restr\gamma+1$ with $X\leq_{\T^\eta}Y$.\footnote{This actually follows from the cofinally many responds, but we include it here for transparency.}
	\item \textsc{Almost disjointness property}: Every level $\T^\eta_\beta$ consists of pairwise almost disjoint sets.\footnote{Two subsets $X,Y\subset\kappa$ are \textit{almost disjoint} if $\abs{X\cap Y}<\kappa$.}
		\item \textsc{Hopeless ideal coherence}: $I_{\bra{}}^{\tau^\eta_\beta}\cap\p(Y)=I_Y^{\tau^\eta_\beta}\cap\p(Y)$ for every $\beta<\alpha$ and $Y\in\T^\eta_\beta$.\\
	\end{itemize}

	Note that what we're really aiming for is achieving the hopeless ideal coherence, since that enables us to ensure that if $X,Y\in\T^\eta$ and $X\subset Y$ then really $X\geq_{\T^\eta}Y$ --- i.e. that we ``catch'' both $X$ and $Y$ in the same play of $\G(\kappa)\restr\eta$. The rest of the properties are inductive properties we need to ensure this.

	\qquad Set $\T^\eta_0:=\{\kappa\}$. Assume that we've built $\T^\eta\restr\alpha+1$ satisfying the inductive assumptions\footnote{In particular, we assume that $\tau^\eta_\alpha$ is defined.} and let $Y\in\T^\eta_\alpha$ --- we need to specify what the $\T^\eta$-successors of $Y$ are. Since $\kappa$ is weakly compact and not measurable it holds by Proposition 6.4 in \cite{Kanamori} that $\text{sat}(I_Y^{\tau^\eta_\alpha})\geq\kappa^+$, so we can fix a maximal antichain $\bra{X_\gamma^Y\mid\gamma<\eta}$ of $I_Y^{\tau^\eta_\alpha}$-positive sets. By $\kappa$-completeness of $I_Y^{\tau^\eta_\alpha}$ we can by Exercise 22.1 in \cite{Jech} even ensure that all of the $X_\gamma^Y$'s are pairwise disjoint.
	
	\qquad To every $\gamma<\eta$ we fix a partial play $p$ of even length of $\G(\kappa)\restr\eta$ consistent with $\tau^\eta_\alpha$ such that the last ordinal $\beta_\gamma^Y$ in $p$ played by player I is greater than or equal to $\gamma$ and $X_\gamma^Y$ has measure one with respect to the last measure in $p$. We then define the $\T^\eta$-successors of $Y$ to be player II's $\tau^\eta_\alpha$-responses to the $\beta_\gamma$'s (which are subsets of the $X_\gamma^Y$'s modulo a bounded set and are therefore pairwise almost disjoint).

  \qquad For limit stages $\delta<\lambda$ we apply $\tau_0$ to the branches of $\T^\eta\restr\delta$ to get $\T^\eta_\delta$.

\qquad We now have to check that the inductive assumptions still hold; let's start with the tree strategy. Assume that we have a partial play $p$ of length $2\cdot\alpha+1$ of $\G(\kappa)\restr\eta$, i.e. the last move in $p$ is by player II, consistent with $\tau^\eta_\alpha$; write $\xi_p$ for player I's last move in $p$ and $Y_p$ for player II's response to $\xi_p$, which is also the last move in $p$. We can then pick a $\zeta<\eta$ such that $\beta_\zeta^{Y_p}>\xi_p$ by the cofinally many responds property and let $\tau^\eta_{\alpha+1}(p)$ be player II's $\tau^\eta_\alpha$-response to the partial play leading up to $\beta_\zeta^{Y_p}$. After this $(\alpha+1)$'th round we just set $\tau^\eta_{\alpha+1}$ to follow $\tau_0$. It's clear that $\tau^\eta_{\alpha+1}$ satisfies the required properties.

  \qquad Before we move on to checking the remaining inductive assumptions, let's pause to get some intuition about the tree strategies. In the definition of $\tau^\eta_{\alpha+1}$ above, we took a partial play consistent with $\tau^\eta_\alpha$, applied $\tau_0$ for a while, took note of player II's last $\tau_0$-response and then included \textit{only that} response in our new $\tau^\eta_{\alpha+1}$ partial play. This means that to every $\tau^\eta_\alpha$-partial play there's an ostensibly much longer $\tau_0$-partial play into which $\tau^\eta_\alpha$ embeds; so we can look at the $\tau^\eta_\alpha$-partial plays as being ``collapsed'' $\tau_0$-partial plays.

	\qquad  Given the above tree strategy, $\T^\eta_{\alpha+1}$ clearly satisfies the cofinally many responds property and the positivity property, simply by construction. For the unique pre-history, let $Y\in\T^\eta_{\alpha+1}$ and assume it has two distinct immediate $\T^\eta$-predecessors $Z_0,Z_1\in\T^\eta_\alpha$. But then $Y\subset Z_0\cap Z_1$ and $Y$ is $I_{Z_0}^{\tau^\eta_\alpha}$-positive by the positivity assumption, contradicting that $Z_0$ and $Z_1$ are almost disjoint by the almost disjointness property. Given the unique pre-history we then also get the almost disjointness property.

\clai{
	$\T^\eta\restr\alpha+2$ satisfies the hopeless ideal coherence property.
}

\cproof{
	Let $Y\in\T^\eta_{\alpha+1}$ --- we have to show that
	\eq{
		I_{\bra{}}^{\tau^\eta_{\alpha+1}}\cap\p(Y)=I_Y^{\tau^\eta_{\alpha+1}}\cap\p(Y).\tag*{$(1)$}
	}

	It's clear that $I_{\bra{}}^{\tau^\eta_{\alpha+1}}\subset I_Y^{\tau^\eta_{\alpha+1}}$, so let $Z\in I_Y^{\tau^\eta_{\alpha+1}}\cap\p(Y)$ and assume for a contradiction that $Z$ is $I_{\bra{}}^{\tau^\eta_{\alpha+1}}$-positive. Letting $\vec\alpha_\xi*\vec Y_\xi$ be a play of $\G(\kappa)\restr\eta$ consistent with $\tau^\eta_{\alpha+1}$ such that $Z$ is in the final measure, the definition of $\tau^\eta_{\alpha+1}$ yields that $Y_\alpha\in\T^\eta_{\alpha+1}$. As $Z\in I_Y^{\tau^\eta_{\alpha+1}}$ we have to assume that $Y\neq Y_\alpha$, so that the almost disjointness property implies that
\eq{
	\abs{Y\cap Y_\alpha}<\kappa,\tag*{$(2)$}
}

By the choice of $\vec\alpha_\xi*\vec Y_\xi$ there's some $\delta\in(\alpha,\lambda)$ such that $\abs{Y_\delta-Z}<\kappa$, i.e. that $Y_\delta$ is a subset of $Z$ modulo a bounded set, since the $Y_\alpha$'s generate the final measure of the play. But then $Y_\delta\subset Y_\alpha$ by the rules of $\G(\kappa)\restr\eta$, and also that $\abs{Y_\delta -Y}<\kappa$ since $Z\subset Y$. But this means that $Y\cap Y_\alpha$ is $I_Y^{\tau^\eta_{\alpha+1}}$-positive since $Y_\delta$ is, contradicting $(2)$. This shows $(1)$.
}
 
\qquad This finishes the construction of $\T^\eta_{\alpha+1}$. For limit levels $\delta<\lambda$ we define $\tau^\eta_\delta$ as simply applying $\tau_0$ to the branches of $\T^\eta\restr\delta$ --- showing that the inductive assumptions hold at $\T^\eta_\delta$ is analogous to the above arguments, so we're now done with the construction of $\T^\eta$. Let $\tau^\eta:=\bigcup_{\alpha<\lambda}\tau^\eta_\alpha\restr{^{<\alpha}H_{\kappa^+}}$ and define\footnote{Note that the tree strategy property above ensures that the strategies \textit{do} line up, so that $\tau^\eta$ is a well-defined strategy as well.} $\I^\eta:=I_{\bra{}}^{\tau^\eta}$.

\qquad Now note that $\I^{\eta+1}\subset\I^\eta$ and $\T^\eta\subset\T^{\eta+1}$ for every $\eta<\kappa^+$ --- set $\I:=\bigcap_{\eta<\kappa^+}\I^\eta$ and $\T:=\bigcup_{\eta<\kappa^+}\T^\eta$. We showed that all hopeless ideals are $\kappa$-complete, normal and $(\kappa,\kappa)$-distributive, so this holds in particular for the $\I^\eta$'s and thus also for $\I$.

\qquad We claim that $\T$ is dense in $\p(\kappa)/\I$.\footnote{This means that given any $\I$-positive set $X$ there's a $Y\in\T$ such that $Y-X\in\I$.} Let $X$ be an $\I$-positive set, making it $\I^\eta$-positive for some $\eta<\kappa^+$, meaning that there's a play $\vec\alpha_\gamma*\tau^\eta$ of $\G(\kappa)\restr\eta$ such that $X$ is in the final measure, which means that $\abs{Y_\delta-X}<\kappa$ for some large $\delta<\lambda$ and in particular that $Y_\delta-X\in\I$. But $Y_\delta\in\T^\eta\subset\T$ by definition of $\tau^\eta$, which shows that $\T$ is dense.

\qquad It remains to show that $\T$ is ${<}\lambda$-closed. If $\lambda=\omega$ then this is trivial, so assume that $\lambda\geq\omega_1$. Let $\beta<\lambda$ and let $\bra{Z_\alpha\mid\alpha<\beta}$ be a $\subset$-decreasing sequence of elements $Z_\alpha\in\T$. We can fix some $\eta<\kappa^+$ such that $Z_\alpha\in\T^\eta$ for every $\alpha<\beta$ by regularity of $\kappa^+$, and since the $Z_\alpha$'s are $\subset$-decreasing they must also be $\leq_{\T^\eta}$-increasing by the hopeless ideal coherence for $\T^\eta$\footnote{This is the only place in which we're using hopeless ideal coherence.}.
	
\qquad Let $\tilde Z\in\T^\eta$ be player II's $\tau^\eta$-response to the unique partial play of $\G(\kappa)\restr\eta$ corresponding to the branch containing the $Z_\alpha$'s, and pick $Z\in\T^\eta$ such that $\abs{Z-\tilde Z}<\kappa$ and $Z\geq_{\T^\eta}Z_\alpha$ for all $\alpha<\beta$, again by the density claim and the hopeless ideal coherence. Then $Z$ witnesses ${<}\lambda$-closure of $\T$.\footnote{We're using that $\lambda$ is regular to get $Z$.}
}

\theo[N.]{
	\label{theo.powerclosed}
	Let $\kappa$ be a regular cardinal and $\lambda\in[\omega_1,\kappa^+]$ be regular. Then the following are equivalent:
	\begin{enumerate}
		\item $\kappa$ is ${<}\lambda$-closed generically power-measurable;
		\item $\kappa$ is ${<}\lambda$-closed ideally power-measurable;
		\item $\kappa$ is $(\kappa,\kappa)$-distributive ${<}\lambda$-closed generically measurable;
		\item $\kappa$ is $(\kappa,\kappa)$-distributive ${<}\lambda$-closed ideally measurable;
		\item Player II has a winning strategy in $\G_\lambda(\kappa)$.
	\end{enumerate}
}
\proof{
	$(v)\Rightarrow (iv)$ is Theorem \ref{theo.hopelessideal} above\footnote{Here wellfoundedness of the generic ultrapower is automatic since $\lambda$ has uncountable cofinality.} and $(iv)\Rightarrow(iii)+(ii)$, $(iii)\Rightarrow(i)$ and $(ii)\Rightarrow(i)$ are trivial, so we show $(i)\Rightarrow(v)$.
	
	\qquad Assume $\kappa$ is ${<}\lambda$-closed generically power-measurable, so there's a ${<}\lambda$-closed forcing $\mathbb P$ and a $V$-generic $g\subset\mathbb P$ such that, in $V[g]$, there exists a transitive class $N$ and a $\kappa$-powerset preserving elementary embedding $\pi\colon V\to N$. Write $\mu$ for the induced weakly amenable $V$-normal $V$-measure on $\kappa$. Now, back in $V$, define a strategy $\sigma$ for player II in $G_\lambda(\kappa)$ as follows.
	
	\qquad Whenever player I plays some model $M_\alpha$ then we let player II respond with a filter $\mu_\alpha$ such that, for some $p_\alpha\in\mathbb P$, $p_\alpha\forces\godel{\check\mu_\alpha=\dot\mu\cap\check M_\alpha}$ --- such a filter exists because $\mu$ is weakly amenable. We require the $p_\alpha$'s to be decreasing, which is possible by ${<}\lambda$-closure. Now, all the $\mu_\alpha$'s are clearly $M_\alpha$-normal $M_\alpha$-measures on $\kappa$, which makes $\sigma$ a winning strategy.
}

Ignoring wellfoundedness we get the same equivalence in the $\lambda=\omega$ case.

\coro[N.]{
	Let $\kappa$ be a regular cardinal. Then the following are equivalent:\footnote{Points $(i)$ and $(ii)$ look a lot like what a definition of generically power-measurable and $(\kappa,\kappa)$-distributive ideally measurable \textit{should} be, but here we're not requiring the ultrapowers to be well-founded, so that would be stretching the definition of being measurable.}
	\begin{enumerate}
		\item There exists a forcing poset $\mathbb P$ such that, in $V^{\mathbb P}$, there's a weakly amenable $V$-normal $V$-measure on $\kappa$;
		\item There exists a $(\kappa,\kappa)$-distributive forcing poset $\mathbb P$ such that, in $V^{\mathbb P}$, there's a $V$-normal $V$-measure on $\kappa$;
		\item $\kappa$ carries a normal $(\kappa,\kappa)$-distributive ideal;
		\item Player II has a winning strategy in $\G_\omega^-(\kappa)$;
		\item $\kappa$ is completely ineffable.
	\end{enumerate}
}
\proof{
	$(iv)\Leftrightarrow (v)$ was shown in \cite{NielsenWelch}, and $(iii)\Rightarrow(ii)$ and $(ii)\Rightarrow(i)$ are trivial. $(i)\Rightarrow(iv)$ is as $(i)\Rightarrow(v)$ in Theorem \ref{theo.powerclosed}, and $(iv)\Rightarrow(iii)$ is Theorem \ref{theo.hopelessideal}.
}

\qcoro{
	``$(\kappa,\kappa)$-distributive ${<}\lambda$-closed'' is ideal-absolute for all regular $\lambda\in[\omega,\kappa^+]$.
}



\subsection{$\lambda$-density \& ${<}\lambda$-closure}

\todo[inline]{Can we get $\kappa$-complete below somehow? In this case, when $\lambda<\kappa$, $\kappa$ cannot be inaccessible and cannot be a successor cardinal, by Kunen's ``Saturated Ideals'' paper.}

\theo[N.]{
  \label{theo.hopelessideal2}
	Let $\kappa$ and $\lambda\leq\kappa^+$ be regular infinite cardinals such that $2^{<\theta}<\kappa$ for every $\theta<\lambda$. If player II has a winning strategy in $\C_\lambda^-(\kappa)$ then $\kappa$ carries a $\lambda$-complete  ideal $\I$ such that $\p(\kappa)/\I$ is forcing equivalent to $\text{Add}(\lambda,1)$.
}
\proof{
	If $\lambda=\kappa^+$ then we're done by Theorem \ref{theo.hopelessideal}, since $\G_{\kappa^+}(\kappa)$ is equivalent to $\C_{\kappa^+}(\kappa)$, so assume that $\lambda\leq\kappa$. We follow the proof of Theorem \ref{theo.hopelessideal} closely. Set $\mathbb P:=\text{Col}(\lambda,2^\kappa)$. Fix a wellordering $<_{\kappa^+}$ of $H_{\kappa^+}$ and a $\mathbb P$-name $\pi$ for a sequence $\bra{\N_\gamma\mid\gamma<\lambda}\in V^{\mathbb P}$ such that
	\begin{itemize}
		\item $\N_\gamma\in V$ for every $\gamma<\lambda$;
		\item $\kappa{+}1\subset\N_\gamma$ and $\abs{\N_\gamma-H_\kappa}^V<\lambda$ for every $\gamma<\lambda$;
		\item If $\delta<\lambda$ is a limit ordinal then $\N_\delta=\bigcup_{\gamma<\delta}\N_\gamma$, $\N_\delta\prec H_{\kappa^+}$ and $\N_\delta\models\zfc^-$;
		\item $\N_\gamma\cup\{\N_\gamma\}\subset\N_\beta$ for all $\gamma<\beta<\lambda$;
		\item $\p(\kappa)^V\subset\bigcup_{\gamma<\lambda}\N_\gamma$.\\
	\end{itemize}

	Define the auxilliary game $\G(\kappa)$ as in the proof of Theorem \ref{theo.hopelessideal} but where player I plays ordinals $\alpha_\eta<\lambda$ and where we use the above $\N_\gamma$'s. Here we only need ${<}\lambda$-closure of $\mathbb P$ to get an equivalence between $\G(\kappa)$ and $\C_\lambda^-(\kappa)$, since $\abs{\N_\gamma-H_\kappa}^V<\lambda$ for all $\gamma<\lambda$.

	\qquad To every limit ordinal $\eta<\lambda$ we define the restricted auxilliary game $\G(\kappa)\restr\eta$ as in the proof of Theorem \ref{theo.hopelessideal}, and to every winning strategy $\tau$ in $\G(\kappa)\restr\eta$ and partial play $p$ of $\G(\kappa)\restr\eta$ consistent with $\tau$ define the associated \textbf{hopeless ideal}\footnote{This terminology is due to Matt Foreman.}
	\eq{
		I_p^\tau\restr\eta:=\{X\subset\kappa\mid\ &\text{For every play $\vec\alpha_\gamma*\tau$ extending $p$ in $\G(\kappa)\restr\eta$,}\\ &\text{$X$ is \textit{not} in the final measure}\}.
	}

	As in the proof of Claim \ref{clai.hopelessideal} we get that every hopeless ideal is $\lambda$-complete.

	\qquad Now, if $\kappa$ is measurable then we trivially get the conclusion,\footnote{Take $\I(\text{Add}(\lambda,1),\check\mu)$ for $\mu$ the measure on $\kappa$.} so assume $\kappa$ isn't measurable. Then $\text{sat}(\kappa)\geq\lambda$ since $2^{<\theta}<\kappa$ for every $\theta<\lambda$,\footnote{See Proposition 16.4 in \cite{Kanamori}.} so that we can continue exactly as in the proof of Theorem \ref{theo.hopelessideal} to construct ($\lambda$-sized) trees $\T^\eta$ and winning strategies $\tau^\eta$ for all limit ordinals $\eta<\lambda$ such that, setting $\I:=\bigcap_{\eta<\lambda}I^{\tau^\eta}_{\bra{}}$ and $\T:=\bigcup_{\eta<\lambda}\T^\eta$, $\T$ is a dense ${<}\lambda$-closed subset of $\p(\kappa)/\I$ of size $\lambda$, so that $\p(\kappa)/\I$ is forcing equivalent to $\text{Add}(\lambda,1)$.
}

\coro[N.]{
	\label{coro.cohen}
	Let $\kappa$ and $\lambda\in[\omega_1,\kappa^+]$ be regular such that $2^{<\theta}<\kappa$ for every $\theta<\lambda$. Then the following are equivalent:
	\begin{enumerate}
		\item $\kappa$ is ${<}\lambda$-closed generically measurable;
		\item $\kappa$ is ${<}\lambda$-closed ideally measurable;
		\item $\kappa$ is ${<}\lambda$-closed $\lambda$-sized generically measurable;
		\item $\kappa$ is ${<}\lambda$-closed $\lambda$-sized ideally measurable;
		\item Player II has a winning strategy in $\C_\lambda(\kappa)$.
	\end{enumerate}
}
\proof{
	$(iv)\Rightarrow (iii)+(ii)$, $(ii)\Rightarrow(i)$ and $(iii)\Rightarrow(i)$ all trivial, and $(i)\Rightarrow(v)$ is like $(i)\Rightarrow(v)$ in Theorem \ref{theo.powerclosed}, and $(v)\Rightarrow(iv)$ is Theorem \ref{theo.hopelessideal2}.
}

Again, if we ignore wellfoundedness then we get the same equivalence in the $\lambda=\omega$ case:

\coro[N.]{
	\label{coro.cohen2}
	Let $\kappa$ be regular infinite. Then:
	\begin{enumerate}
		\item Player II has a winning strategy in $\C_\omega^-(\kappa)$; and
		\item $\kappa$ carries an ideal $I$ such that $\p(\kappa)/I$ is forcing equivalent to $\text{Add}(\omega,1)$.
	\end{enumerate}
}
\proof{
	Player II has a winning strategy in $\C_\omega^-(\kappa)$ as we're simply measuring finitely many sets without any demand for wellfoundedness, showing $(i)$. Since $2^{<n}<\kappa$ for all $n<\omega$ as $\kappa$ is infinite, Theorem \ref{theo.hopelessideal2} then implies $(ii)$.
}

\qcoro{
	``${<}\lambda$-closed $\lambda$-sized'' is ideal-absolute for all regular $\lambda\in[\omega,\kappa^+]$.
}


\subsection*{$(\omega,\alpha)$-Ramsey cardinals}

A natural generalisation of the $\gamma$-Ramsey definition is to require more iterability of the last measure. Of course, by Proposition \ref{prop.tildegame} we have that $\G_\gamma(\kappa,\zeta)$ is equivalent to $\G_\gamma(\kappa)$ when $\cof\gamma>\omega$ so the next definition is only interesting whenever $\cof\gamma=\omega$.

\defi[N.]{
	Let $\alpha,\beta$ be ordinals. Then a cardinal $\kappa$ is \textbf{$(\alpha,\beta)$-Ramsey} if player I does not have a winning strategy in $\G_\alpha^\theta(\kappa,\beta)$ for all regular $\theta>\kappa$.\footnote{Note that an $\alpha$-Ramsey cardinal is the same as an $(\alpha,0)$-Ramsey cardinal.}
}

\defi[Gitman]{
	A cardinal $\kappa$ is \textbf{$\alpha$-iterable} if for every $A\subset\kappa$ there exists a \textit{transitive} weak $\kappa$-model $\M$ with $A\in\M$ and an $\alpha$-good $\M$-measure $\mu$ on $\M$.
}

\prop{
	\label{prop.ramseyit}
	If $\beta>0$ then every $(\alpha,\beta)$-Ramsey is a $\beta$-iterable stationary limit of $\beta$-iterables.
}
\proof{
	Let $(\M,\in,\mu)$ be a result of a play of $\G_\alpha^{\kappa^+}(\kappa,\beta)$ in which player II won. Then the transitive collapse of $(\M,\in,\mu)$ witnesses that $\kappa$ is $\beta$-iterable, since $\mu$ is $\beta$-good by definition of $\G_\alpha^{\kappa^+}(\kappa,\beta)$.
	
	\qquad That $\kappa$ is $\beta$-iterable is reflected to some $H_\theta$, so let now $(\N,\in,\nu)$ be a result of a play of $\G_\alpha^\theta(\kappa,\beta)$ in which player II won. Then $\N\prec H_\theta$, so that $\kappa$ is also $\beta$-iterable in $\N$. Since being $\beta$-iterable is witnessed by a subset of $\kappa$ and $\beta>0$ implies\footnote{Recall that $\beta$-good for $\beta>0$ in particular implies weak amenability.} that we get a $\kappa$-powerset preserving $j:\N\to\P$, $\P$ also thinks that $\kappa$ is $\beta$-iterable, making $\kappa$ a stationary limit of $\beta$-iterables by elementarity.
}

We now move towards Theorem \ref{theo.upperlimit} which gives an upper consistency bound for the $(\omega,\alpha)$-Ramseys. We first recall a few definitions and a folklore lemma.

\defi{
	For an infinite ordinal $\alpha$, a cardinal $\kappa$ is \textbf{$\alpha$-Erd\H os} for $\alpha\leq\kappa$ if given any club $C\subset\kappa$ and regressive $c:[C]^{<\omega}\to\kappa$ there is a set $H\in[C]^\alpha$ homogeneous for $c$; i.e. that $\abs{c``[H]^n}\leq 1$ holds for every $n<\omega$.
}

\defi{
	\label{defi.remind}
	A set of indiscernibles $I$ for a structure $\M=(M,\in,A)$ is \textbf{remarkable} if $I-\iota$ is a set of indiscernibles for $(M,\in,A,\bra{\xi\mid\xi<\iota})$ for every $\iota\in I$.
}

\lemm[Folklore]{
	\label{lemma}
	Let $\kappa$ be $\alpha$-Erd\H os where $\alpha\in[\omega,\kappa]$ and let $C\subset\kappa$ be club. Then any structure $\M$ in a countable language $\mathcal L$ with $\kappa+1\subset\M$ has a remarkable set of indiscernibles $I\in[C]^\alpha$.
}
\proof{
	Let $\bra{\varphi_n\mid n<\omega}$ enumerate all $\mathcal L$-formulas and define $c:[C]^{<\omega}\to\kappa$ as follows. For an increasing sequence $\alpha_1<\cdots<\alpha_{2n}\in C$ let
	\eq{
		c(\{\alpha_1,\hdots,\alpha_{2n}\}):=&\text{ the least }\lambda<\alpha_1\text{ such that }\\
    &\exists\delta_1<\cdots\delta_k\exists m<\omega:\lambda=\bra{m,\delta_1,\hdots,\delta_k}\land\\
		&\M\not\models\varphi_m[\vec\delta,\alpha_1,\hdots,\alpha_n]\leftrightarrow\varphi_m[\vec\delta,\alpha_{n+1},\hdots,\alpha_{2n}]
	}

	if such a $\lambda$ exists, and $c(s)=0$ otherwise. Clearly $c$ is regressive, so since $\kappa$ is $\alpha$-Erd\H os we get a homogeneous $I\in[C]^\alpha$ for $c$; i.e. that $\abs{c``[I]^n}\leq 1$ for every $n<\omega$. Then $c(\{\alpha_1,\hdots,\alpha_{2n}\})=0$ for every $\alpha_1,\hdots,\alpha_{2n}\in I$, as otherwise there exists an $m<\omega$ and $\delta_1<\cdots\delta_k$ such that for any $\alpha_1<\hdots<\alpha_{2n}\in I$,
	\eq{
		\M\not\models\varphi_m[\vec\delta,\alpha_1,\hdots,\alpha_n]\leftrightarrow\varphi_m[\vec\delta,\alpha_{n+1},\hdots,\alpha_{2n}].\tag*{$(\dagger)$}
	}
	
	But then simply pick $\alpha_1<\hdots\alpha_{2n}<\alpha_1'<\cdots<\alpha_{2n}'$ so that both $\{\alpha_1,\hdots,\alpha_{2n}\}$ and $\{\alpha_1',\hdots,\alpha_{2n}'\}$ witnesses $(\dagger)$; then either $\{\alpha_1,\hdots,\alpha_n,\alpha_1',\alpha_n'\}$ or \\$\{\alpha_1,\hdots,\alpha_n,\alpha_{n+1}',\hdots,\alpha_{2n}'\}$ also witnesses that $(\dagger)$ fails, $\contr$.
}

\theo[N.]{
	\label{theo.upperlimit}
	Let $\alpha\in[\omega,\omega_1]$ be additively closed. Then any $\alpha$-Erd\H os cardinal is a limit of $(\omega,\alpha)$-Ramsey cardinals.
}
\proof{
	Let $\kappa$ be $\alpha$-Erd\H os, $\theta>\kappa$ a regular cardinal and $\beta<\kappa$ any ordinal. Use the above Lemma \ref{lemma} to get a set of remarkable indiscernibles $I\in[\kappa]^\alpha$ for the structure $(H_\theta,\in,\bra{\xi\mid\xi<\beta})$, and let $\iota\in I$ be the least indiscernible in $I$. We will show that player I has no winning strategy in $\G_\omega^\theta(\iota,\alpha)$, so by the proof of Theorem 5.5(d) in \cite{HolySchlicht} it suffices to find a weak $\iota$-model $\M\prec H_\theta$ and an $\alpha$-good $\M$-measure on $\iota$. Define
	\eq{
		\M:=\hull^{H_\theta}(\iota\cup I)\prec H_\theta
	}
	
	and let $\pi:I\to I$ be the right-shift map. Since $I$ is remarkable, $I$ ($=I-\iota$) is a set of indiscernibles for the structure $(H_\theta,\in,\bra{\xi\mid\xi<\iota})$, so that $\pi$ induces an elementary embedding $j:\M\to\M$ with $\crit j=\iota$, given as
	\eq{
		j(\tau^{\M}[\vec\xi,\iota_{i_0},\hdots,\iota_{i_k}]):=\tau^{\M}[\vec\xi,\iota_{i_0+1},\hdots,\iota_{i_k+1}],
	}

	with $\vec\xi\subset\iota$. Since $j$ is trivially $\iota$-powerset preserving we get that $\M\prec H_\theta$ is a weak $\iota$-model satisfying $\zfc^-$ with a 1-good $\M$-measure $\mu_j$ on $\iota$. Furthermore, as we can linearly iterate $\M$ simply by applying $j$ we get an $\alpha$-iteration of $\M$ since there are $\alpha$-many indiscernibles. Note that at limit stages $\gamma<\alpha$ our iteration sends $\tau^{\M}[\vec\xi,\iota_{i_0},\hdots,\iota_{i_k}]$ to $\tau^{\M}[\vec\xi,\iota_{i_0+\gamma},\hdots,\iota_{i_k+\gamma}]$ so here we are using that $\alpha$ is additively closed.
	
	\qquad This shows that player I has no winning strategy in $\G_\omega^\theta(\iota,\alpha)$. Since $\iota>\beta$ and $\beta<\kappa$ was arbitrary, $\kappa$ is a limit of $\eta$ such that player I has no winning strategy in $\G_\omega^\theta(\eta,\alpha)$. If we repeat this procedure for all regular $\theta>\kappa$ we get by the pidgeon hole principle that $\kappa$ is a limit of $(\omega,\alpha)$-Ramsey cardinals.
}

As Theorem 4.5 in \cite{GitmanSchindler} shows that $(\alpha{+}1)$-iterable cardinals have $\alpha$-Erd\H os cardinals below them for $\alpha\geq\omega$ additively closed, this shows that the $(\omega,\alpha)$-Ramseys form a strict hierarchy. Further, as $\alpha$-Erd\H os cardinals are consistent with $V=L$ when $\alpha<\omega_1^L$ and $\omega_1$-iterable cardinals aren't consistent with $V=L$, we also get that $(\omega,\alpha)$-Ramsey cardinals are consistent with $V=L$ if $\alpha<\omega_1^L$ and that they aren't if $\alpha=\omega_1$.


\subsection*{[Strategic] $(\omega{+}1)$-Ramsey cardinals}

The next step is then to consider $(\omega{+}1)$-Ramseys, which turn out to cause a considerable jump in consistency strength. We first need the following result which is implicit in \cite{Mitchell} and in the proof of Lemma 1.3 in \cite{Kapplications} --- see also \cite{Dodd} and \cite{Ramsey1}.

\qtheo[Dodd, Mitchell]{
	\label{theo.ramseycondition}
	A cardinal $\kappa$ is Ramsey if and only if every $A\subset\kappa$ is an element of a weak $\kappa$-model $\M$ such that there exists a weakly amenable countably complete $\M$-measure on $\kappa$.
}

The following theorem then supplies us with a lower bound for the strength of the $(\omega{+}1)$-Ramsey cardinals. It should be noted that a better lower bound will be shown in Theorem \ref{theo.plusone}, but we include this Ramsey lower bound as well for completeness.

\theo[N.]{
	\label{theo.ramlimram}
	Every $(\omega{+}1)$-Ramsey cardinal is a Ramsey limit of Ramseys.
}
\proof{
	Let $\kappa$ be $(\omega{+}1)$-Ramsey and $A\subset\kappa$. Let $\sigma$ be a strategy for player I in $\G_{\omega+1}^{\kappa^+}(\kappa)$ satisfying that whenever $\vec\M_\alpha*\vec\mu_\alpha$ is consistent with $\sigma$ it holds that $A\in\M_0$ and $\mu_\alpha\in\M_{\alpha+1}$ for all $\alpha\leq\omega$. Then $\sigma$ isn't winning as $\kappa$ is $(\omega{+}1)$-Ramsey, so we may fix a play $\sigma*\vec\mu_\alpha$ of $\G_{\omega+1}^{\kappa^+}(\kappa)$ in which player II wins. Then by the choice of $\sigma$ we get that $\mu_\omega$ is a weakly amenable $\M_\omega$-measure on $\kappa$, and by the rules of $\G_{\omega+1}^{\kappa^+}(\kappa)$ it's also countably complete (it's even normal), which makes $\kappa$ Ramsey by the above Theorem \ref{theo.ramseycondition}.

	\qquad Since $\kappa$ is Ramsey, $\M_\omega\models\godel{\kappa\text{ is Ramsey}}$ as well. Letting $j:\M_\omega\to\N$ be the $\kappa$-powerset preservering embedding induced by $\mu_\omega$, we also get that $\N\models\godel{\kappa\text{ is Ramsey}}$ by $\kappa$-powerset preservation. This then implies that $\kappa$ \textit{is} a stationary limit of Ramsey cardinals inside $\M_\omega$, and thus also in $V$ by elementarity.
}

As for the \textit{consistency} strength of the strategic $(\omega{+}1)$-Ramsey cardinals, we get the following result that they reach a measurable cardinal. The proof of the following is closely related to the proof due to Silver and Solovay that player II having a winning strategy in the \textit{cut and choose game} is equiconsistent with a measurable cardinal --- see e.g. p. 249 in \cite{c&c}.

\theo[N.]{
	\label{theo.omegaplusone}
	If $\kappa$ is a strategic $(\omega{+}1)$-Ramsey cardinal then, in $V^{\col(\omega,2^\kappa)}$, there's a transitive class $N$ and an elementary embedding $j:V\to N$ with $\crit j=\kappa$. In particular, the existence of a strategic $(\omega{+}1)$-Ramsey cardinal is equiconsistent with the existence of a measurable cardinal.
}
\proof{
	Set $\mathbb P:=\col(\omega,2^\kappa)$ and let $\sigma$ be player II's winning strategy in $\G_{\omega+1}^{\kappa^+}(\kappa)$. Let $\dot\M$ be a $\mathbb P$-name of an $\omega$-sequence $\bra{\M_n\mid n<\omega}$ of weak $\kappa$-models $\M_n\in V$ such that $\M_n\prec H_{\kappa^+}^V$ and $\p(\kappa)^V\subset\bigcup_{n<\omega}\M_n$, and let $\dot\mu$ be a $\mathbb P$-name for the $\omega$-sequence of $\sigma$-responses to the $\M_n$'s in $\G_{\omega+1}^{\kappa^+}(\kappa)^V$.

	\qquad Assume that there's a $\mathbb P$-condition $p$ which forces the generic ultrapower $\ult(V,\bigcup_n\dot\mu_n)$ to be illfounded, meaning that we can fix a $\mathbb P$-name $\dot f$ for an $\omega$-sequence $\bra{f_n\mid n<\omega}$ such that
	\eq{
		p\forces\dot X_n:=\{\alpha<\kappa\mid\dot f_{n+1}(\alpha)<\dot f_n(\alpha)\}\in\bigcup_{n<\omega}\dot\mu_n.
	}

	Now, in $V$, we fix some large regular $\theta\gg\kappa$ and a countable $\N\prec H_\theta$ such that $\dot\M,\dot\mu,\dot f,H_{\kappa^+}^V,\sigma,p\in\N$. We can find an $\N$-generic $g\subset\mathbb P^{\N}$ in $V$ with $p\in g$ since $\N$ is countable, so that $\N[g]\in V$. But the play $\dot\M^g_n*\dot\mu^g_n$ is a play of $\G_\omega^{\kappa^+}(\kappa)^V$ which is according to $\sigma$, meaning that $\bigcup_{n<\omega}\dot\mu^g_n$ is normal and in particular countably complete (in $V$). Then $\bigcap_{n<\omega}\dot X_n^g\neq\emptyset$, but if $\alpha\in\bigcap_{n<\omega}\dot X_n^g$ then $\bra{\dot f^g_n(\alpha)\mid n<\omega}$ is a strictly decreasing $\omega$-sequence of ordinals, $\contr$. This means that $\ult(V,\bigcup_n\mu_n)$ is indeed wellfounded.

	\qquad This conclusion is well-known to imply that $\kappa$ is a measurable in an inner model; see e.g. Lemma 4.2 in \cite{KellnerShelah}.
}

The above Theorem \ref{theo.omegaplusone} then answers Question 9.2 in \cite{HolySchlicht} in the negative, asking if $\lambda$-Ramseys are strategic $\lambda$-Ramseys for uncountable cardinals $\lambda$, as well as answering Question 9.7 from the same paper in the positive, asking whether strategic fully Ramseys are equiconsistent with a measurable.



\subsection{The general case}

\subsection*{Gitman's cardinals}

In this subsection we define the strongly- and super Ramsey cardinals from \cite{Ramsey1} and investigate further connections between these and the $\alpha$-Ramsey cardinals. First, a definition.

\defi[Gitman]{
	A cardinal $\kappa$ is \textbf{strongly Ramsey} if every $A\subset\kappa$ is an element of a transitive $\kappa$-model $\M$ with a weakly amenable $\M$-normal $\M$-measure $\mu$ on $\kappa$. If furthermore $\M\prec H_{\kappa^+}$ then we say that $\kappa$ is \textbf{super Ramsey}.
}

Note that since the model $\M$ in question is a \textit{$\kappa$-model} it is closed under countable sequences, so that the measure $\mu$ is automatically countably complete. The definition of the strongly Ramseys is thus exactly the same as the characterisation of Ramsey cardinals, with the added condition that the model is closed under ${<}\kappa$-sequences. \cite{Ramsey1} shows that every super Ramsey cardinal is a strongly Ramsey limit of strongly Ramsey cardinals, and that $\kappa$ is strongly Ramsey iff every $A\subset\kappa$ is an element of a transitive $\kappa$-model $\M\models\zfc$ with a weakly amenable $\M$-normal $\M$-measure $\mu$ on $\kappa$.

\qquad Now, a first connection between the $\alpha$-Ramseys and the strongly- and super Ramseys is the result in \cite{HolySchlicht} that fully Ramsey cardinals are super Ramsey limits of super Ramseys. The following result then shows that the strongly- and super Ramseys are sandwiched between the almost fully Ramseys and the fully Ramseys.

\theo[N.-Welch]{
  Every strongly Ramsey cardinal is a stationary limit of almost fully Ramseys.
}
\proof{
  Let $\kappa$ be strongly Ramsey and let $\M\models\zfc$ be a transitive $\kappa$-model with $V_\kappa\in\M$ and $\mu$ a weakly amenable $\M$-normal $\M$-measure. Let $\gamma<\kappa$ have uncountable cofinality and $\sigma\in\M$ a strategy for player I in $\G_\gamma(\kappa)^{\M}$. Now, whenever player I plays $\M_\alpha\in\M$ let player II play $\mu\cap\M_\alpha$, which is an element of $\M$ by weak amenability of $\mu$. As $\M^{<\kappa}\subset\M$ the resulting play is inside $\M$, so $\M$ sees that $\sigma$ is not winning.

	\qquad Now, letting $j_\mu:\M\to\N$ be the induced embedding, $\kappa$-powerset preservation of $j_\mu$ implies that $\mu$ is also a weakly amenable $\N$-normal $\N$-measure on $\kappa$. This means that we can copy the above argument to ensure that $\kappa$ is also almost fully Ramsey in $\N$, entailing that it is a stationary limit of almost fully Ramseys in $\M$. But note now that $\lambda$ is almost fully Ramsey iff it is almost fully Ramsey in a transitive $\zfc$-model containing $H_{(2^\lambda)^+}$ as an element by Theorem 5.5(e) in \cite{HolySchlicht}, so that $\kappa$ being inaccessible, $V_\kappa\in\M$ and $\M$ being transitive implies that $\kappa$ really \textit{is} a stationary limit of almost fully Ramseys.
}


\subsection*{Downwards absoluteness to $K$}

Lastly, we consider the question of whether the $\alpha$-Ramseys are downwards absolute to $K$, which turns out to at least be true in many cases. The below Theorem \ref{theo.downK} then also answers Question 9.4 from \cite{HolySchlicht} in the positive, asking whether $\alpha$-Ramseys are downwards absolute to the Dodd-Jensen core model for $\alpha\in[\omega,\kappa]$ a cardinal. We first recall the definition of $0^\pistol$.

\defi{
	$0^\pistol$ is ``the sharp for a strong cardinal'', meaning the minimal sound active mouse $\M$ with $\M\l\crit(\dot F^{\M})\models\godel{\text{There exists a strong cardinal}}$, with $\dot F^{\M}$ being the top extender of $\M$.
}

\theo[N.-Welch]{
	\label{theo.downK}
	Assume $0^\pistol$ does not exist. Let $\lambda$ be a limit ordinal with uncountable cofinality and let $\kappa$ be $\lambda$-Ramsey. Then $K\models\godel{\kappa\text{ is a $\lambda$-Ramsey cardinal}}$.
}
\proof{
	Note first that $\kappa^{+K}=\kappa^+$ by \cite{SchindlerCovering}, since $\kappa$ in particular is weakly compact.	Let $\sigma\in K$ be a strategy for player I in $\G_\lambda^{\kappa^+}(\kappa)^K$, so that a play following $\sigma$ will produce weak $\kappa$-models $\M\prec K\l\kappa^+$. We can then define a strategy $\tilde\sigma$ for player I in $\G_\lambda^{\kappa^+}(\kappa)$ as follows. Firstly let $\tilde\sigma(\emptyset):=\hull^{H_{\kappa^+}}(K\l\kappa\cup\sigma(\emptyset))$. Assuming now that $\bra{\tilde\M_\alpha,\tilde\mu_\alpha\mid\alpha<\gamma}$ is a partial play of $\G_\lambda^{\kappa^+}(\kappa)$ which is consistent with $\tilde\sigma$, we have two cases. If $\tilde\mu_\alpha\in K$ for every $\alpha<\gamma$ then let $\bra{\M_\alpha\mid\alpha<\gamma}$ be the corresponding models played in $\G_\lambda^{\kappa^+}(\kappa)^K$ from which the $\tilde\M_\alpha$'s are derived and let
	\eq{
		\tilde\sigma(\bra{\tilde\M_\alpha,\tilde\mu_\alpha\mid\alpha<\gamma}):=\hull^{H_{\kappa^+}}(K\l\kappa\cup\sigma(\bra{\M_\alpha,\tilde\mu_\alpha\mid\alpha<\gamma})),
	}

	and otherwise let $\tilde\sigma$ play arbitrarily. As $\kappa$ is $\lambda$-Ramsey (in $V$) there exists a play $\bra{\tilde\M_\alpha,\tilde\mu_\alpha\mid\alpha\leq\lambda}$ of $\G_\lambda^{\kappa^+}(\kappa)$ which is consistent with $\tilde\sigma$ in which player II won. Note that $\tilde\M_\lambda\cap K\l\kappa^+\prec K\l\kappa^+$ so let $\N$ be the transitive collapse of $\tilde\M_\lambda\cap K\l\kappa^+$. But if $j:\N\to K\l\kappa^+$ is the uncollapse then $\crit j$ is both an $\N$-cardinal and also $>\kappa$ because we ensured that $K\l\kappa\subset\N$. This means that $j=\id$ because $\kappa$ is the largest $\N$-cardinal by elementarity in $K\l\kappa^+$, so that $\tilde\M_\lambda\cap K\l\kappa^+=\N$ is a transitive elementary substructure of $K\l\kappa^+$, making it an initial segment of $K$.
	
	\qquad Now, since $\mu:=\tilde\mu_\lambda$ is a countably complete weakly amenable $K\l o(\N)$-measure\footnote{Here we use that $\N\pinit K$.}, the ``beaver argument''\footnote{See Lemmata 7.3.7--7.3.9 and 8.3.4 in \cite{Zeman} for this argument.} shows that $\mu\in K$, so that we can then define a strategy $\tau$ for player II in $\G_\lambda^{\kappa^+}(\kappa)^K$ as simply playing $\mu\cap\N\in K$ whenever player I plays $\N$. Since $\mu=\tilde\mu_\lambda$ we also have that $\mu\cap\M_\alpha=\tilde\mu_\alpha\cap\M_\alpha$, so that $\sigma$ will eventually play $\N$, making $\tau$ win against $\sigma$.\footnote{Note that $\tau$ is not necessarily a winning strategy --- all we know is that it is winning against this particular strategy $\sigma$.}
}

Note that the only thing we used $\cof\lambda>\omega$ for in the above proof was to ensure that $\mu$ was countably complete. If now $\kappa$ instead was either genuine- or normal $\alpha$-Ramsey for any limit ordinal $\alpha$ then $\mu_\alpha$ would also be countably complete and weakly amenable, so the same proof shows the following.

\qcoro[N.-Welch]{
	\label{coro.downK}
	Assume $0^\pistol$ does not exist and let $\alpha$ be any limit ordinal. Then every genuine- and every normal $\alpha$-Ramsey cardinal is downwards absolute to $K$. In particular, if $\alpha$ is a limit of limit ordinals then every ${<}\alpha$-Ramsey cardinal is downwards absolute to $K$ as well.
}


\subsection*{Indiscernible games}

We now move to the strategic versions of the $\alpha$-Ramsey hierarchy. The first thing we want to do is define \textit{$\alpha$-very Ramsey cardinals}, introduced in \cite{SharpeWelch}, and show the tight connection between these and the strategic $\alpha$-Ramseys. We need a few more definitions. Recall the definition of a remarkable set of indiscernibles from Definition \ref{defi.remind}.

\defi{
	A \textbf{good set of indiscernibles} for a structure $\M$ is a set $I\subset\M$ of remarkable indiscernibles for $\M$ such that $\M\l\iota\prec\M$ for any $\iota\in I$.
}

\defi[Sharpe-Welch]{
	Define the \textbf{indiscernible game} $G^I_\gamma(\kappa)$ in $\gamma$ many rounds as follows
	\game{\M_0}{I_0}{\M_1}{I_1}{\M_2}{I_2}{\cdots}{\cdots}

	Here $\M_\alpha$ is an amenable structure of the form $(J_\kappa[A],\in,A)$ for some $A\subset\kappa$, $I_\alpha\in[\kappa]^\kappa$ is a good set of indiscernibles for $\M_\alpha$ and the $I_\alpha$'s are $\subset$-decreasing. Player II wins iff they can continue playing through all the rounds.
}

\defi[Sharpe-Welch]{
	A cardinal $\kappa$ is \textbf{$\gamma$-very Ramsey} if player II has a winning strategy in the game $G^I_\gamma(\kappa)$.
}

The next couple of results concerns the connection between the strategic $\alpha$-Ramseys and the $\alpha$-very Ramseys. We start with the following.

\theo[N.]{
	\label{theo.plusone}
	Every $(\omega{+}1)$-Ramsey is an $\omega$-very Ramsey stationary limit of $\omega$-very Ramseys.
}
\proof{
	Let $\kappa$ be $(\omega{+}1)$-Ramsey. We will describe a winning strategy for player II in the indiscernible game $G_\omega^I(\kappa)$. If player I plays $\M_0=(J_\kappa[A_0],\in,A_0)$ in $G_\omega^I(\kappa)$ then let player I in $\G_{\omega+1}^{\kappa^+}(\kappa)$ play
	\eq{
		\h_0:=\hull^{H_{\kappa^+}}(J_\kappa[A_0]\cup\{\M_0,\kappa,A_0\})\prec H_{\kappa^+}.
	}

	Let player I now follow a strategy in $\G_{\omega+1}^{\kappa^+}(\kappa)$ which starts off with $\h_0$ and ensures that, whenever $\vec\M_\alpha*\vec\mu_\alpha$ is consistent with player I's strategy, then $\mu_\alpha\in\M_{\alpha+1}$ for all $\alpha\leq\omega$. Since player II is not losing in $\G_{\omega+1}^{\kappa^+}(\kappa)$ there is a play $\vec\M_\alpha*\vec\mu_\alpha$ in which player I follows this strategy just described and where player II wins -- write $\h_0^{(\alpha)}:=\M_\alpha$ and $\mu_0^{(\alpha)}:=\mu_\alpha$ for the models and measures in this play.
	\game{\h_0^{(0)}}{\mu_0^{(0)}}{\cdots}{\cdots}{\h_0^{(\omega)}}{\mu_0^{(\omega)}}{\h_0^{(\omega+1)}}{\mu_0^{(\omega+1)}}

	By the choice of player I's strategy we get that $\mu_0^{(\omega)}$ is both weakly amenable, and it's also countably complete by the rules of $\G_{\omega+1}^{\kappa^+}(\kappa)$ (it's even normal). Now Lemma 2.9 of \cite{SharpeWelch} gives us a set of good indiscernibles $I_0\in\mu_0^{(\omega)}$ for $\M_0$, as $\M_0\in\h_0^{(\omega)}$ and $\mu_0^{(\omega)}$ is a countably complete weakly amenable $\h_0^{(\omega)}$-normal $\h_0^{(\omega)}$-measure on $\kappa$. Let player II play $I_0$ in $G_\omega^I(\kappa)$. Let now $\M_1=(J_\kappa[A_1],\in,A_1)$ be the next play by player I in $G_\omega^I(\kappa)$.
	\game{\M_0}{I_0}{\M_1}{}{}{}{}{}

	Since $\mu_0^{(\omega)}=\bigcup_n\mu_0^{(n)}$ we must have that $I_0\in\mu_0^{(n_0)}$ for some $n_0<\omega$. In the $(n_0{+}1)$'st round of $\G_{\omega+1}^{\kappa^+}(\kappa)$ we change player I's strategy and let player I play
	\eq{
		\h_1:=\hull^{H_{\kappa^+}}(J_\kappa[A_0]\cup\{\M_0,\M_1,\kappa,A_0,A_1,\bra{\h_0^{(k)},\mu_0^{(k)}\mid k\leq n_0}\})\prec H_{\kappa^+}
	}

	and otherwise continues following some strategy, as long as the measures played by player II keep being elements of the following models.	Our play of the game $\G_{\omega+1}^{\kappa^+}(\kappa)$ thus looks like the following so far.

	\game{\h_0^{(0)}}{\mu_0^{(0)}}{\cdots}{\cdots}{\h_0^{(n_0)}}{\mu_0^{(n_0)}}{\h_1}{}

	Now player II in $\G_{\omega+1}^{\kappa^+}(\kappa)$ is not losing at round $n_0$, so there is a play extending the above in which player I follows their revised strategy and in which player II wins. As before we get a set $I_1'\in\mu_1^{(n_1)}$ of good indiscernibles for $\M_1$, where $n_1<\omega$. Since $I_0\in\mu_0^{(n_0)}\subset\mu_1^{(n_1)}$ we can let player II in $G_\omega^I(\kappa)$ play $I_1:=I_0\cap I_1'\in\mu_1^{(n_1)}$. Continuing like this, player II can keep playing throughout all $\omega$ rounds of $G_\omega^I(\kappa)$, making $\kappa$ $\omega$-very Ramsey.

	\qquad As for showing that $\kappa$ is a stationary limit of $\omega$-very Ramseys, let $\M\prec H_{\kappa^+}$ be a weak $\kappa$-model with a weakly amenable countably complete $\M$-normal $\M$-measure $\mu$ on $\kappa$, which exists by Theorem \ref{theo.ramlimram} as $\kappa$ is $(\omega{+}1)$-Ramsey. Then by elementarity $\M\models\godel{\kappa\text{ is $\omega$-very Ramsey}}$ and since $\kappa$ being $\omega$-very Ramsey is absolute between structures having the same subsets of $\kappa$ it also holds in the $\mu$-ultrapower, meaning that $\kappa$ is a stationary limit of $\omega$-very Ramseys by elementarity. 
}

The above proof technique can be generalised to the following.

\theo[N.]{
	\label{theo.stratvery}
	For limit ordinals $\alpha$, every coherent ${<}\omega\alpha$-Ramsey is $\omega\alpha$-very Ramsey.
}
\proof{
	This is basically the same proof as the proof of Theorem \ref{theo.plusone}. We do the ``going-back'' trick in $\omega$-chunks, and at limit stages we continue our non-losing strategy in $\G_{\omega\alpha}^{\kappa^+}(\kappa)$ by using our winning strategy, which we have available as we are assuming coherent ${<}\omega\alpha$-Ramseyness. We need $\alpha$ to be a limit ordinal for this to work, as otherwise we would be in trouble in the last $\omega$-chunk, as we cannot just extend the play to get a countably complete measure, which we need to use the proof of Theorem \ref{theo.plusone}.
}

As for going from the $\alpha$-very Ramseys to the strategic $\alpha$-Ramseys we got the following.

\theo[N.]{
	\label{theo.succverystrat}
	For $\gamma$ any ordinal, every coherent ${<}\gamma$-very Ramsey\footnote{Here the coherency again just means that the winning strategies $\sigma_\alpha$ for player II in $G_\alpha^I(\kappa)$ are $\subset$-increasing.} is coherent ${<}\gamma$-Ramsey.\footnote{Here a ``coherent ${<}\gamma$-very Ramsey cardinal'' is defined from $\gamma$-very Ramseys in the same way as coherent ${<}\gamma$-Ramsey cardinals is defined from $\gamma$-Ramseys. When $\gamma$ is a limit ordinal then coherent ${<}\gamma$-very Ramseys are precisely the same as $\gamma$-very Ramseys, so this is solely to ``subtract one'' when $\gamma$ is a successor ordinal --- i.e. a coherent ${<}(\gamma+1)$-very Ramsey cardinal is the same thing as a $\gamma$-very Ramsey cardinal.}
}
\proof{
	The reason why we work with ${<}\gamma$-Ramseys here is to ensure that player II only has to satisfy a closed game condition (i.e. to continue playing throughout all the rounds). If $\gamma=\beta+1$ then set $\zeta:=\beta$ and otherwise let $\zeta:=\gamma$. Let $\kappa$ be $\zeta$-very Ramsey and let $\tau$ be a winning strategy for player II in $G_\zeta^I(\kappa)$. Let $\M_\alpha\prec H_\theta$ be any move by player I in the $\alpha$'th round of $\G_\zeta(\kappa)$. Let $A_\alpha\subset\kappa$ encode all subsets of $\kappa$ in $\M_\alpha$ and form now
	\eq{
		\N_\alpha:=(J_\kappa[A_\alpha],\in,A_\alpha),
	}

	which is a legal move for player I in $G_\zeta^I(\kappa)$, yielding a good set of indiscernibles $I_\alpha\in[\kappa]^\kappa$ for $\N_\alpha$ such that $I_\alpha\subset I_\beta$ for every $\beta<\alpha$. Now by section 2.3 in \cite{SharpeWelch} we get a structure $\P_\alpha$ with $\N_\alpha\in\P_\alpha$ and a $\P_\alpha$-measure $\tilde\mu_\alpha$ on $\kappa$, generated by $I_\alpha$.\footnote{By \textit{generated} here we mean that $X\in\tilde\mu_\alpha$ iff $X$ contains a tail of indiscernibles from $I_\alpha$.} Set $\mu_\alpha:=\tilde\mu_\alpha\cap\M_\alpha$ and let player II play $\mu_\alpha$ in $\G_\zeta(\kappa)$.

	\qquad As the $\mu_\alpha$'s are generated by the $I_\alpha$'s, the $\mu_\alpha$'s are $\subset$-increasing. We have thus created a strategy for player II in $\G_\zeta(\kappa)$ which does not lose at any round $\alpha<\gamma$, making $\kappa$ coherent ${<}\gamma$-Ramsey.
}

The following result is then a direct corollary of Theorems \ref{theo.stratvery} and \ref{theo.succverystrat}.

\qcoro[N.]{
	\label{coro.verystrat}
	For limit ordinals $\alpha$, $\kappa$ is $\omega\alpha$-very Ramsey iff it is coherent ${<}\omega\alpha$-Ramsey. In particular, $\kappa$ is $\lambda$-very Ramsey iff it is strategic $\lambda$-Ramsey for any $\lambda$ with uncountable cofinality.
}

We can now use this equivalence to transfer results from the $\alpha$-very Ramseys over to the strategic versions. The \textit{completely Ramsey cardinals} are the cardinals topping the hierarchy defined in \cite{Feng}. A completely Ramsey cardinal implies the consistency of a Ramsey cardinal, see e.g. Theorem 3.51 in \cite{SharpeWelch}. We are going to use the following characterisation of the completely Ramsey cardinals, which is Lemma 3.49 in \cite{SharpeWelch}.

\qtheo[Sharpe-Welch]{
	\label{theo.comvery}
	A cardinal is completely Ramsey if and only if it is $\omega$-very Ramsey.
}

This, together with Theorem \ref{theo.plusone}, immediately yields the following strengthening of Theorem \ref{theo.ramlimram}.

\qcoro[N.]{
	Every $(\omega{+}1)$-Ramsey cardinal is a completely Ramsey stationary limit of completely Ramsey cardinals.
}

The above Theorem \ref{theo.succverystrat} also yields the following consequence.

\coro[N.]{
	Every completely Ramsey cardinal is completely ineffable.
}
\proof{
	From Theorem \ref{theo.comvery} we have that being completely Ramsey is equivalent to being $\omega$-very Ramsey, so the above Theorem \ref{theo.succverystrat} then yields that a completely Ramsey cardinal is coherent ${<}\omega$-Ramsey, which we saw in Theorem \ref{theo.ineff} is equivalent to being completely ineffable.
}

Now, moving to the uncountable case, Corollary \ref{coro.verystrat} yields that strategic $\omega_1$-Ramsey cardinals are $\omega_1$-very Ramsey, and Theorem 3.50 in \cite{SharpeWelch} states that $\omega_1$-very Ramseys are measurable in the core model $K$, assuming $0^\pistol$ doesn't exist, which then shows the following theorem. We also include the original direct proof of that theorem, due to Welch.

\theo[Welch]{
	\label{theo.stratramsey}
	Assuming $0^\pistol$ doesn't exist, every strategic $\omega_1$-Ramsey cardinal is measurable in $K$.
}
\proof{
	Let $\kappa$ be strategic $\omega_1$-Ramsey, say $\tau$ is the winning strategy for player II in $\G_{\omega_1}(\kappa)$. Jump to $V[g]$, where $g\subset\col(\omega_1,\kappa^+)$ is $V$-generic. Since $\col(\omega_1,\kappa^+)$ is $\omega$-closed, $V$ and $V[g]$ have the same countable sequences of $V$, so $\tau$ is still a strategy for player II in $\G_{\omega_1}(\kappa)^{V[g]}$, as long as player I only plays elements of $V$.
	
	\qquad Now let $\bra{\kappa_\alpha\mid\alpha<\omega_1}$ be an increasing sequence of regular $K$-cardinals cofinal in $\kappa^+$, let player I in $\G_{\omega_1}(\kappa)$ play $\M_\alpha:=\hull^{H_\theta}(K\l\kappa_\alpha)\prec H_\theta$ and player II follow $\tau$. This results in a countably complete weakly amenable $K$-measure $\mu_{\omega_1}$, which the ``beaver argument''\footnote{See Lemmata 7.3.7--7.3.9 and 8.3.4 in \cite{Zeman} for this argument.} then shows is actually an element of $K$, making $\kappa$ measurable in $K$.
}

A natural question is whether this behaviour persists when going to larger core models. It turns out that the answer is affirmative: every strategic $\omega_1$-Ramsey cardinal is also measurable in Steel's core model below a Woodin, a result due to Schindler which we include with his permission here. We will need the following special case of Corollary 3.1 from \cite{SchindlerIterates}.\footnote{That paper assumes the existence of a measurable as well, but by \cite{JensenSteel} we can omit that here.}

\qtheo[Schindler]{
  \label{theo.Schindler}
  Assume that there exists no inner model with a Woodin cardinal, let $\mu$ be a measure on a cardinal $\kappa$, and let $\pi:V\to\ult(V,\mu)\cong N$ be the ultrapower embedding. Assume that $N$ is closed under countable sequences. Write $K^N$ for the core model constructed inside $N$. Then $K^N$ is a normal iterate of $K$, i.e. there is a normal iteration tree $\T$ on $K$ of successor length such that $\M_{\infty}^{\T}=K^N$. Moreover, we have that $\pi_{0\infty}^{\T}=\pi\restr K$.
}

\theo[Schindler]{
	\label{theo.Schindlerstrat}
  Assuming there exists no inner model with a Woodin cardinal, every strategic $\omega_1$-Ramsey cardinal is measurable in $K$.
}
\proof{
	Fix a large regular $\theta\gg 2^\kappa$. Let $\kappa$ be strategic $\omega_1$-Ramsey and fix a winning strategy $\sigma$ for player II in $\G_{\omega_1}(\kappa)$. Let $g\subset\col(\omega_1,2^\kappa)$ be $V$-generic and in $V[g]$ fix an elementary chain $\bra{M_\alpha\mid\alpha<\omega_1}$ of weak $\kappa$-models $M_\alpha\prec H_\theta^V$ such that $M_\alpha\in V$, $^\omega M_\alpha\subset M_{\alpha+1}$ and $H_{\kappa^+}^V\subset M_{\omega_1}:=\bigcup_{\alpha<\omega_1}M_\alpha$.

	\qquad Note that $V$ and $V[g]$ have the same countable sequences since $\col(\omega_1,2^\kappa)$ is ${<}\omega_1$-closed, so we can apply $\sigma$ to the $M_\alpha$'s, resulting in an $M_{\omega_1}$-measure $\mu$ on $\kappa$. Let $j:M_{\omega_1}\to\ult(M_{\omega_1},\mu)$ be the ultrapower embedding. Since we required that $^\omega M_\alpha\subset M_{\alpha+1}$ we get that $\M_{\omega_1}$ is closed under $\omega$-sequences in $V[g]$, making $\mu$ countably complete in $V[g]$. As we also ensured that $H_{\kappa^+}^V\subset\M_{\omega_1}$ we can lift $j$ to an ultrapower embedding $\pi:V\to\ult(V,\mu)\cong N$ with $N$ transitive.
	
	\qquad Since $V$ is closed under $\omega$-sequences in $V[g]$ we get by standard arguments that $N$ is as well, which means that Theorem \ref{theo.Schindler} applies, meaning that $\pi\restr K:K\to K^N$ is an iteration map with critical point $\kappa$, making $\kappa$ measurable in $K$.
}

\end{document}
