\documentclass[../main]{subfiles}
\pagestyle{fancy}

\begin{document}

\chapter{Ideals}
\label{apx.ideals}
\thispagestyle{fancy}

\defi{
  Let $I$ be an ideal on a nonempty set $Z$. Let
  \begin{enumerate}
    \item $I^{+} := \mathcal{P}(Z) \setminus I$,
    \item for $a,b \in I^{+}$ let $a \sim_{I} b$ iff $a \Delta b \in I$,
    \item $\mathcal{P}(Z)/I:=\P(Z)/{\sim_I}$ is the Boolean algebra
      with subset inclusion modulo $\sim_I$.
  \end{enumerate}

  We call $\P(Z)/I$ the \index{Ideal!Forcing associated to an ideal}
  \emph{associated forcing} to $I$.
}

\defi{
  If $I$ is an ideal on a cardinal $\kappa$ and
  $g\subset\P(\kappa)/I$ $V$-generic then $g$ is a $V$-ultrafilter on
  $\kappa$ in $V[g]$, so that we may take the \index{Ideal!Generic ultrapower by an ideal}\index{Generic
    ultrapower} \emph{generic ultrapower} $\ult(V,g)$.
}

\prop{
  Let $I$ be an ideal on a cardinal $\kappa$. Then..
  \begin{enumerate}
    \item if $I$ is $\kappa$-complete then so is any generic ultrafilter;
    \item if $I$ is normal then so is any generic ultrafilter.$\hfill\dashv$
    \end{enumerate}
    \todo{define $\kappa$-complete and normal for an ideal. Add reference.}
}

\begin{definition}
  Let $\lambda$ be any cardinal. Then an ideal $I$ on a cardinal
  $\kappa$ is...
  \begin{itemize}
  \item \index{Precipitous ideal}\index{Ideal!Precipitous ideal} \emph{precipitous} if the generic
    ultrapower is wellfounded;
  \item \index{Saturated ideal}\index{Ideal!Saturated ideal} \emph{$\lambda$-saturated}
    if the associated forcing has the $\lambda$-chain condition;
  \item \index{Dense ideal}\index{Ideal!Dense ideal} \emph{$\lambda$-dense} if the
    associated forcing has a dense subset of size
    $\lambda$.$\hfill\dashv$
  \end{itemize}
\end{definition}

Note that $\lambda$-dense trivially implies
$\lambda^+$-saturated. We'll need the following facts about
$\omega_2$-saturated ideals on $\omega_1$:

\begin{proposition}\todo{Parts (ii)-(v) is Example 4.29 in Foreman's
    handbook chapter. Perhaps include the proof.}
  \label{prop.ideal}
  Let $I$ be an $\omega_2$-saturated ideal on $\omega_1$. Then $I$ is
  precipitous, and letting $j \colon V\to M$ be the generic ultrapower map,
  it holds that
  \begin{enumerate}
    \item $M$ is closed under $\omega$-sequences in $V[g]$;
    \item $j(\omega_1^V)=\omega_2^V=\omega_1^{V[g]}$;
    \item $j(\omega_2^V)\in(\omega_2^V,\omega_3^V)$;
    \item $j$ is continuous at $\omega_2^V$;
    \item $j(\omega_n^V)=\omega_n^V=\omega_{n-1}^{V[g]}$ for all
      $n\in[3,\omega]$.$\hfill\dashv$
  \end{enumerate}
\end{proposition}

As for the density, we in particular need the following fact:

\qprop{ Let $I$ be an $\omega_1$-dense ideal on $\omega_1$. Then the
  associated forcing is forcing equivalent to $\col(\omega,\omega_1)$,
  so in particular it's homogeneous.
}

\proof{
  \cite[Proposition~10.20]{Kanamori}.
}


\end{document}
